Odd one out and non-verbal communication
========================================================

---
author: Andrés Gómez Emilsson

date: May 14 2014

participants: 200
---

![alt text]['sd']


```{r}

patch <- read.csv("/Users/andesgomez/Documents/Stanford/Autumn2013-Masters/PayedWork/andres_data/Spring2014/patch_oddone_no_fam_14_may_PATCH.csv",
                           header=TRUE, sep="\t", row.names=NULL, stringsAsFactors = FALSE)

patch$odd_one <- patch$Answer.choice=="\"odd_one\""
patch$twin_1 <- patch$Answer.choice=="\"twin_1\""
patch$twin_2 <- patch$Answer.choice=="\"twin_2\""

compliant <- patch$Answer.manip_check_target == "\"2\"" & patch$Answer.manip_check_dist == "\"2\"" & patch$Answer.manip_check_foil == "\"2\"" & patch$Answer.name_check_correct == "\"TRUE\""
patch_compliant <- subset(patch,compliant)

length(patch$Answer.item)



```



```{r echo=FALSE}
# Compliant test 
compliant <- patch$Answer.manip_check_target == "\"2\"" & patch$Answer.manip_check_dist == "\"2\"" & patch$Answer.manip_check_foil == "\"2\"" & patch$Answer.name_check_correct == "\"TRUE\""
patch_compliant <- subset(patch,compliant)

# Number of compliant participants
print("number of compliant participants")
print(length(patch_compliant$Answer.item))

patch$odd_one <- patch$Answer.choice=="\"odd_one\""
patch$twin_1 <- patch$Answer.choice=="\"twin_1\""
patch$twin_2 <- patch$Answer.choice=="\"twin_2\""



patch_subset = subset(patch_compliant, patch_compliant$Answer.linguistic_framing_condition == 9)
word_subset = subset(patch_compliant, patch_compliant$Answer.linguistic_framing_condition == 10)

patch_table <- aggregate(cbind(odd_one,
                                  twin_1,
                                  twin_2) ~ 
                           Answer.linguistic_framing_condition , data=patch_compliant, sum)

# People choosing the odd one out
points_to_patch = patch_table[1,2] / sum(patch_table[1,2:4])


## Demographic processing

patch_compliant$males = patch_compliant$Answer.gender == "\"m\"" | patch_compliant$Answer.gender == "\"male\"" | patch_compliant$Answer.gender == "\"M\"" | patch_compliant$Answer.gender == "\"Male\"" | patch_compliant$Answer.gender == "\"MALE\""
patch_compliant$females = patch_compliant$Answer.gender == "\"f\"" | patch_compliant$Answer.gender == "\"female\"" | patch_compliant$Answer.gender == "\"F\"" | patch_compliant$Answer.gender == "\"Female\"" | patch_compliant$Answer.gender == "\"FEMALE\""

patch_compliant$twenties =  patch_compliant$Answer.age == "\"20\"" | patch_compliant$Answer.age == "\"21\"" | patch_compliant$Answer.age == "\"22\"" | patch_compliant$Answer.age == "\"23\"" | patch_compliant$Answer.age == "\"24\"" | patch_compliant$Answer.age == "\"25\"" | patch_compliant$Answer.age == "\"26\"" | patch_compliant$Answer.age == "\"27\"" | patch_compliant$Answer.age == "\"28\"" | patch_compliant$Answer.age == "\"29\"" 
patch_compliant$thirties = patch_compliant$Answer.age == "\"30\"" | patch_compliant$Answer.age == "\"31\"" | patch_compliant$Answer.age == "\"32\"" | patch_compliant$Answer.age == "\"33\"" | patch_compliant$Answer.age == "\"34\"" | patch_compliant$Answer.age == "\"35\"" | patch_compliant$Answer.age == "\"36\"" | patch_compliant$Answer.age == "\"37\"" | patch_compliant$Answer.age == "\"38\"" | patch_compliant$Answer.age == "\"39\"" 
patch_compliant$fourties = patch_compliant$Answer.age == "\"40\"" | patch_compliant$Answer.age == "\"41\"" | patch_compliant$Answer.age == "\"42\"" | patch_compliant$Answer.age == "\"43\"" | patch_compliant$Answer.age == "\"44\"" | patch_compliant$Answer.age == "\"45\"" | patch_compliant$Answer.age == "\"46\"" | patch_compliant$Answer.age == "\"47\"" | patch_compliant$Answer.age == "\"48\"" | patch_compliant$Answer.age == "\"49\"" 
patch_compliant$fifties = patch_compliant$Answer.age == "\"50\"" | patch_compliant$Answer.age == "\"51\"" | patch_compliant$Answer.age == "\"52\"" | patch_compliant$Answer.age == "\"53\"" | patch_compliant$Answer.age == "\"54\"" | patch_compliant$Answer.age == "\"55\"" | patch_compliant$Answer.age == "\"56\"" | patch_compliant$Answer.age == "\"57\"" | patch_compliant$Answer.age == "\"58\"" | patch_compliant$Answer.age == "\"59\""


#colorblind-friendly color palettes
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")


```






```{r}
# Statistical analysis - (regressions, anova, chi square, factor analysis, etc.)

summary(aov(odd_one ~  Answer.linguistic_framing_condition * Answer.item, data = patch_compliant))


summary(glm(odd_one ~  Answer.linguistic_framing_condition + twenties, data = patch_compliant))


```




```{r}
# Visualization - the reason this is after statistical analysis is that some properties of the graphs (e.g. a regression line or confidence intervals) are in themselves statistical analysis computed in the previous section

library(plyr)
library(reshape2)
library(ggplot2)
library(binom)
library(bootstrap)





#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}




# Plot the histogram for the answers given on each item (aggreagating linguistic frame conditions)
#ms <- aggregate(odd_one ~ Answer.linguistic_framing_condition + Answer.item, data = patch_compliant,l.mean)

#ms$cil <- aggregate(odd_one ~ Answer.linguistic_framing_condition + Answer.item, data = patch_compliant, l.ci.low)$odd_one
#ms$cih <- aggregate(odd_one ~ Answer.linguistic_framing_condition + Answer.item, data = patch_compliant, l.ci.high)$odd_one



md <- melt(patch_compliant, measure.vars = c("odd_one","twin_1","twin_2"), variable.name="object", value.name="chosen")


ms <- ddply(md, .(object, Answer.item), #Answer.item, 
            summarise, 
            c = mean(chosen),
            n = sum(chosen), 
            l = length(chosen),
            sdc = sd(chosen),
            c.cih = c + l.ci.high(chosen),
            c.cil = c - l.ci.low(chosen))


ms$item <- factor(ms$Answer.item)
levels(ms$item) <- c("boat","friend", "pizza", "snowman", "sundae", "Christmas tree")

ggplot(ms, aes(x= item, y=c, fill=object)) + 
  geom_bar(position=position_dodge()) + 
  geom_linerange(aes(ymin=c.cil,ymax=c.cih), 
                 position=position_dodge(width=.9)) + 
  ylab("Probability of choosing") +
  scale_fill_manual(values=cbPalette)



# Visualizing the two conditions separately: Show the histogram by item and by condition

ms <- ddply(patch_compliant, .(Answer.linguistic_framing_condition,Answer.item),
      function(x) {
        y <- data.frame(choice=c("odd_one","twin_1","twin_2"),
                        proportion=c(mean(x$odd_one),mean(x$twin_1),mean(x$twin_2)))
        return(y)
      })

ms$frame <- factor(ms$Answer.linguistic_framing_condition)
levels(ms$frame) <- c("patch","word")
ms$item <- factor(ms$Answer.item)

qplot(item, proportion, fill=choice, facets = . ~ frame, 
      geom="bar",
      data=ms)

patch_table <- aggregate(cbind(odd_one,
                               twin_1,
                               twin_2) ~ 
                           Answer.linguistic_framing_condition , data=patch_compliant, sum)



```





Complete Basic info:

May 14th 2014

200 subjects | 3FC | NO familiarization | random out of 6 | Linguistic framing: One 
word or color patch | Participants asked to count the tshree elements
scale, level 1
Code: PATCH

patch_oddone_no_fam_14_may_PATCH.csv

var participant_response_type = 0;

var participant_feature_count = 2; // They count all of the props

var linguistic_framing = random(9,10); // 

var question_type = 0;

var target_filler_sequence = 0;

var familiarization_status = 0;

var stim_index = random(0,5);

var scale_and_level = 8;

var img_size = 200; // needs to be implemented, currently just a placeholder   

var cond = random(1,4);

var file_number_to_use_for_referents = '3'

render("odd_one.Rmd", "pdf_document")

#/Users/andesgomez/Documents/Stanford/Autumn2013-Masters/PayedWork/RMarkdown_files
#Rscript -e "require(knitr); require(markdown); knit('$odd_one.rmd', '$odd_one.md'); #markdownToHTML('$odd_one.md', '$odd_one.html')"

pandoc -s odd_one.html -o odd_one.html.pdf


['sd']: /Users/andesgomez/Documents/Stanford/Autumn2013-Masters/PayedWork/pragmods/cleanPragmods/experiments_in_pictures/odd_one_out_linguisticFraming9.png