---
title: "combined_analysis"
author: "Avery Katko"
date: "August 12, 2014"
output: pdf_document
---

```{r}
rm(list=ls())
library(ggplot2)
library(reshape2)
library(plyr)
library(bootstrap)
setwd("~/Documents/pragmods")
#source("useful.R")
d.seq <- read.csv("seq_data/pragmods_seq.anondata.csv")
d.wx3 <- read.csv("seq_data/pragmods_wx3.anondata.csv")
d.bx3 <- read.csv("seq_data/pragmods_bx3.anondata.csv")
d.seq2 <- read.csv("seq_data/pragmods_seq2.anondata.csv")
d.L2second <- read.csv("seq_data/pragmods_L2second.anondata.tsv",sep="\t")
raw.list <- list(d.seq, d.wx3, d.bx3, d.seq2, d.L2second)
```

Exclude participants that either failed manipulation check or were rejected.

```{r}
exclude.seq <- d.seq$assignmentstatus == "Rejected" |
  d.seq$Answer.name_check_correct == "\"FALSE\""
d.seq <- subset(d.seq, exclude.seq == FALSE)

exclude.wx3 <- d.wx3$assignmentstatus == "Rejected" |
  d.wx3$Answer.name_check_correct == "\"FALSE\""
d.wx3 <- subset(d.wx3, exclude.wx3 == FALSE)

exclude.bx3 <- d.bx3$assignmentstatus == "Rejected" |
  d.bx3$Answer.name_check_correct == "\"FALSE\""
d.bx3 <- subset(d.bx3, exclude.bx3 == FALSE)

exclude.seq2 <- d.seq2$assignmentstatus == "Rejected" |
  d.seq2$Answer.name_check_correct == "\"FALSE\""
d.seq2 <- subset(d.seq2, exclude.seq2 == FALSE)

exclude.L2second <- d.L2second$assignmentstatus == "Rejected" |
  d.L2second$Answer.name_check_correct == "\"FALSE\""
d.L2second <- subset(d.L2second, exclude.L2second == FALSE)
```

Choice correct as logical factors

```{r}
d.seq$Answer.choice_correct_1 <- factor(as.logical(d.seq$Answer.choice_correct_1))
d.seq$Answer.choice_correct_2 <- factor(as.logical(d.seq$Answer.choice_correct_2))
d.seq$Answer.choice_correct_3 <- factor(as.logical(d.seq$Answer.choice_correct_3))

d.wx3$Answer.choice_correct_1 <- factor(as.logical(d.wx3$Answer.choice_correct_1))
d.wx3$Answer.choice_correct_2 <- factor(as.logical(d.wx3$Answer.choice_correct_2))
d.wx3$Answer.choice_correct_3 <- factor(as.logical(d.wx3$Answer.choice_correct_3))
d.wx3$Answer.choice_correct_4 <- factor(as.logical(d.wx3$Answer.choice_correct_4))
d.wx3$Answer.choice_correct_5 <- factor(as.logical(d.wx3$Answer.choice_correct_5))
d.wx3$Answer.choice_correct_6 <- factor(as.logical(d.wx3$Answer.choice_correct_6))

d.bx3$Answer.choice_correct_1 <- factor(as.logical(d.bx3$Answer.choice_correct_1))
d.bx3$Answer.choice_correct_2 <- factor(as.logical(d.bx3$Answer.choice_correct_2))
d.bx3$Answer.choice_correct_3 <- factor(as.logical(d.bx3$Answer.choice_correct_3))
d.bx3$Answer.choice_correct_4 <- factor(as.logical(d.bx3$Answer.choice_correct_4))
d.bx3$Answer.choice_correct_5 <- factor(as.logical(d.bx3$Answer.choice_correct_5))
d.bx3$Answer.choice_correct_6 <- factor(as.logical(d.bx3$Answer.choice_correct_6))

d.seq2$Answer.choice_correct_1 <- factor(as.logical(d.seq2$Answer.choice_correct_1))
d.seq2$Answer.choice_correct_2 <- factor(as.logical(d.seq2$Answer.choice_correct_2))
d.seq2$Answer.choice_correct_3 <- factor(as.logical(d.seq2$Answer.choice_correct_3))

d.L2second$Answer.choice_correct_1 <- factor(as.logical(d.L2second$Answer.choice_correct_1))
d.L2second$Answer.choice_correct_2 <- factor(as.logical(d.L2second$Answer.choice_correct_2))
d.L2second$Answer.choice_correct_3 <- factor(as.logical(d.L2second$Answer.choice_correct_3))
```

Restructure data to have trial and level variables. (working around mturk data submission limitations; can't safely submit arrays, so we have to use separate variables for each trial)

```{r}
d.seq$level_1 <- factor(ifelse(d.seq$Answer.sequence_condition == "\"1w0w1b\"",1,0))
d.seq$level_2 <- factor(ifelse(d.seq$Answer.sequence_condition == "\"1w0w1b\"",0,1))
d.seq$level_3 <- factor(rep(1,nrow(d.seq)))

d.wx3$level_1 <- factor(rep(0,nrow(d.wx3)))
d.wx3$level_2 <- factor(rep(1,nrow(d.wx3)))
d.wx3$level_3 <- factor(rep(0,nrow(d.wx3)))
d.wx3$level_4 <- factor(rep(1,nrow(d.wx3)))
d.wx3$level_5 <- factor(rep(0,nrow(d.wx3)))
d.wx3$level_6 <- factor(rep(1,nrow(d.wx3)))

d.bx3$level_1 <- factor(rep(0,nrow(d.bx3)))
d.bx3$level_2 <- factor(rep(1,nrow(d.bx3)))
d.bx3$level_3 <- factor(rep(0,nrow(d.bx3)))
d.bx3$level_4 <- factor(rep(1,nrow(d.bx3)))
d.bx3$level_5 <- factor(rep(0,nrow(d.bx3)))
d.bx3$level_6 <- factor(rep(1,nrow(d.bx3)))

d.seq2$level_1 <- factor(ifelse(d.seq2$Answer.sequence_condition == "\"0w1w2w\"",0,2))
d.seq2$level_2 <- factor(rep(1,nrow(d.seq2)))
d.seq2$level_3 <- factor(ifelse(d.seq2$Answer.sequence_condition == "\"0w1w2w\"",2,0))

d.L2second$level_1 <- factor(ifelse(d.L2second$Answer.sequence_condition == "\"0w2w1w\"",0,1))
d.L2second$level_2 <- factor(rep(2,nrow(d.L2second)))
d.L2second$level_3 <- factor(ifelse(d.L2second$Answer.sequence_condition == "\"0w2w1w\"",1,0))

trial.df <- function(d,tn){
  df <- data.frame(id = d$workerid,
                   seqCond = d$Answer.sequence_condition,
                   trial = factor(rep(tn,nrow(d))),
                   level = d[sprintf("level_%d",tn)],
                   item = d[sprintf("Answer.item_%d",tn)],
                   targetProp = d[sprintf("Answer.target_prop_%d",tn)],
                   distractorProp = d[sprintf("Answer.distractor_prop_%d",tn)],
                   targetPosition = d[sprintf("Answer.target_position_%d",tn)],
                   distractorPosition = d[sprintf("Answer.distractor_position_%d",tn)],
                   choice = d[sprintf("Answer.choice_%d",tn)],
                   choiceCorrect = d[sprintf("Answer.choice_correct_%d",tn)])
  names(df) <- c("id","seqCond","trial","level","item","targetProp","distractorProp",
                 "targetPosition","distractorPosition","choice","choiceCorrect")
  return(df)
}

df <- rbind(trial.df(d.seq,1),trial.df(d.seq,2),trial.df(d.seq,3),
            trial.df(d.wx3,1),trial.df(d.wx3,2),trial.df(d.wx3,3),trial.df(d.wx3,4),trial.df(d.wx3,5),trial.df(d.wx3,6),
            trial.df(d.bx3,1),trial.df(d.bx3,2),trial.df(d.bx3,3),trial.df(d.bx3,4),trial.df(d.bx3,5),trial.df(d.bx3,6),
            trial.df(d.seq2,1),trial.df(d.seq2,2),trial.df(d.seq2,3),
            trial.df(d.L2second,1),trial.df(d.L2second,2),trial.df(d.L2second,3))

df$seqCondAndTrial <- sprintf("%s[%s]",df$seqCond,df$trial)

summary(df)
```

```{r}
#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}

ms <- aggregate(choiceCorrect ~ seqCond + trial + level,data = df,l.mean)
ms$cil <- aggregate(choiceCorrect ~ seqCond + trial + level, data = df, l.ci.low)$choiceCorrect
ms$cih <- aggregate(choiceCorrect ~ seqCond + trial + level, data = df, l.ci.high)$choiceCorrect

ms2 <- aggregate(choiceCorrect ~ seqCondAndTrial + seqCond + level,data = df,l.mean)
ms2$cil <- aggregate(choiceCorrect ~ seqCondAndTrial + level, data = df, l.ci.low)$choiceCorrect
ms2$cih <- aggregate(choiceCorrect ~ seqCondAndTrial + level, data = df, l.ci.high)$choiceCorrect

#colorblind-friendly color palettes
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Compare performance in each condition for each inference level

```{r}
ggplot(data = ms2, aes(x = seqCondAndTrial, y = choiceCorrect, fill = seqCond)) +
  geom_bar(stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = choiceCorrect - cil, ymax = choiceCorrect + cih), width = 0.2) +
  facet_grid(level ~ .) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x=element_text(angle = -90, hjust = 0))
```

Compare level 2 expts

```{r}
ms.L2 <- subset(ms2,grepl("2w",seqCond))
levels(ms.L2$seqCond) <- c("aaa","bbb","ccc","ddd","0,1,2","2,1,0","0,2,1","1,2,0")
ggplot(data = ms.L2, aes(x = seqCond, y = choiceCorrect, fill = seqCond)) +
  geom_bar(stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = choiceCorrect - cil, ymax = choiceCorrect + cih), width = 0.2) +
  facet_grid(. ~ level) +
  theme_bw() +
  scale_fill_manual(values=cbPalette) +
  theme(axis.text.x=element_text(angle = 0, hjust = 0)) +
  xlab("order condition") +
  ylab("proportion chose target")
```
