---
title: "Levels analysis"
author: "Mike Frank"
date: "November 5, 2014"
output: pdf_document
---
  
```{r}
rm(list=ls())
source("../helper.R")
source("../useful_dplyr.R")
```

Level of recursion
----
  
```{r}
d1 <- read.turk("../../data/3-levels/levels/scale_plus_6stimuli_3levels_no_fam_24_january_SCAL.tsv")
d2 <- read.turk("../../data/3-levels/levels/scales_6stimuli_3levels_no_fam_25_january_OSCA.tsv")
d3 <- read.turk("../../data/3-levels/levels/forced_choice_no_fam_6random_count_onewordmumble_22jan2015_SCALESBASE.tsv")

d1$cond <- "complex"
d2$cond <- "simple"
d3$cond <- "complex prior"
d3$level <- -1
d1 <- d1 %>% rename(level = scale_and_levels_condition) %>% mutate(level = level -2)
d2 <- d2 %>% rename(level = scale_and_levels_condition)
d <- rbind_list(d1,d2, d3) 
```

Counts and exclusions.

```{r}
d %>% group_by(cond, level) %>%
  summarise(n=length(workerid), 
            mc.targ = mean(as.numeric(mc.targ, na.rm=TRUE)),
            mc.dist = mean(as.numeric(mc.dist, na.rm=TRUE)))

mcs <- data.frame(cond = c("simple","simple",
                           "complex","complex","complex", 
                           "complex prior"), 
                  level = c(0,1,0,1,2,-1), 
                  mc.targ.ans = c(1, NA, 1, 2, 2, 2),
                  mc.dist.ans = c(2, 1, 2, 2, 1, 1))

d <- left_join(d, mcs)

d %>% group_by(cond,level) %>%
  summarise(n=length(workerid))

dc <- d %>% filter(is.na(mc.targ.ans) | as.numeric(mc.targ) == mc.targ.ans,
                   as.numeric(mc.dist) == mc.dist.ans,
                   mc.name == "TRUE")

dc %>% group_by(cond,level) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  group_by(cond, level) %>%
  summarise(correct = mean(choice == "target"),             
            cih = ci.high(choice == "target"),
            cil = ci.low(choice == "target"))

ms$cond <- factor(ms$cond, levels=c("simple","complex"))
ms$level <- factor(ms$level)

pdf("../../plots/3-levels-levels.pdf",width=6, height=3.5)
qplot(level, correct, geom=c("bar","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, fill=factor(level),
      facets=.~cond, 
      data=filter(ms,level!="-1")) 
dev.off()
```

Models

```{r}
dc %>%  
  group_by(cond, level, choice) %>%
  summarise(n = n()) %>%
  spread(choice, n)
```

"Twins" displays
----
  
Files:

* mistake: used favorite "scaleweird_6stimuli_no_fam_favorite_19_february_WERF.csv"
* scaleweird_6stimuli_no_fam_oneword_19_february_WERD.csv
  
```{r}
d <- read.turk("data/3-levels/twins/scaleweird_6stimuli_no_fam_oneword_19_february_WERD.csv")
d <- d %>% rename(cond = scale_and_levels_condition) %>% 
  mutate(cond = factor(c("twin feature","uniform feature")[cond - 5]))
```

Counts and exclusions.

```{r}
d %>% group_by(cond) %>%
  summarise(n=length(workerid), 
            mc.targ = mean(as.numeric(mc.targ, na.rm=TRUE)),
            mc.dist = mean(as.numeric(mc.dist, na.rm=TRUE)))

mcs <- data.frame(cond = c("twin feature","uniform feature"), 
                  mc.targ.ans = c(2, 3),
                  mc.dist.ans = c(1, 1))

d <- left_join(d, mcs)

d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc <- d %>% filter(is.na(mc.targ.ans) | as.numeric(mc.targ) == mc.targ.ans,
                   as.numeric(mc.dist) == mc.dist.ans,
                   mc.name == "TRUE")

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  group_by(cond) %>%
  summarise(correct = mean(choice == "twin"),             
            cih = ci.high(choice == "twin"),
            cil = ci.low(choice == "twin"))

pdf("plots/3-levels-twins.pdf",width=4.5, height=3.5)
qplot(cond, correct, geom=c("bar","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, fill=cond,
      data=ms) + 
  ylab("Proportion choosing either twin face") + 
  xlab("Target feature")
dev.off()
```


"Odd man" displays
----
  
Files:

* patch_oddone_no_fam_14_may_PATCH.csv
  
```{r}
d <- read.turk("data/3-levels/oddman/patch_oddone_no_fam_14_may_PATCH.csv")
d <- d %>% rename(cond = ling.cond) %>% 
  mutate(cond = factor(c("patch","word")[cond - 8]))
```

Counts and exclusions.

```{r}
dc <- d %>% filter(as.numeric(mc.targ) == 2,
                   as.numeric(mc.dist) == 2,
                   mc.name == "TRUE")

d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  group_by(cond) %>%
  summarise(correct = mean(choice == "odd_one"),             
            cih = ci.high(choice == "odd_one"),
            cil = ci.low(choice == "odd_one"))

pdf("plots/3-levels-oddman.pdf",width=4.5, height=3.5)
qplot(cond, correct, geom=c("bar","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, fill=cond,
      data=ms) + 
  ylab("Proportion choosing non-literal interpretation") + 
  xlab("Target feature") + 
  ylim(c(0,1))
dev.off()
```





Distractor experiment
----

Done by Benjamin Gittelson

Files (representing three differnet data collection sweeps): 

* pragmods_distractions.results1.tsv
* pragmods_distractions.results2.tsv
* pragmods_distractions.results3.tsv

```{r}
d1 <- read.turk("data/4-size/pragmods_distractions.results1.tsv")
d2 <- read.turk("data/4-size/pragmods_distractions.results2.tsv")
d3 <- read.turk("data/4-size/pragmods_distractions.results3.tsv")

d <- rbind_list(d1,d2,d3) 
```

Merge condition. 

```{r}
conds <- read.csv("data/4-size/scale_and_level.csv")

d <- left_join(d,conds,by="scale_and_levels_condition")
```

Counts and exclusions. Note that this experiment has no manipulation check (Must check whether it has a manipulation check at all!). 

```{r}
d %>% group_by(target.level, objects, features) %>%
  summarise(n=length(workerid), 
            mc.targ = mean(as.numeric(mc.targ, na.rm=TRUE)),
            mc.dist = mean(as.numeric(mc.dist, na.rm=TRUE)))

dc <- d %>% filter(mc.name == "TRUE")

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  group_by(scale_and_levels_condition,targ.features, objects, features) %>%
  summarise(correct = mean(choice == "target"),             
            cih = ci.high(choice == "target"),
            cil = ci.low(choice == "target"))

ms$targ.features <- factor(ms$targ.features)
ms$features <- factor(ms$features)
# pdf("plots/4-size-dists.pdf",width=6, height=3.5)
qplot(targ.features, correct, geom=c("bar","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, fill=targ.features,
      facets = objects ~ features,
      data=ms) 
# dev.off()
```

Another plot:

```{r}
pdf("plots/4-size-dists.pdf",width=8, height=4)
qplot(objects, correct, geom=c("line","pointrange"), 
      ymin=correct - cil, ymax=correct + cih, col=features,
      position=position_dodge(width=.1),
      data=ms) + facet_grid(.~ targ.features) +
  ylim(c(0,1))
dev.off()
```

Some regression:

```{r}
d$correct <- d$choice == "target"
summary(glm(correct ~ objects * features, 
            data=filter(d, targ.features == 2)))
summary(glm(correct ~ objects + features, 
            data=filter(d, targ.features == 2)))
```