---
title: "Prelims analysis"
author: "Mike Frank"
date: "November 5, 2014"
output: html_document
---

```{r}
rm(list=ls())
source("../helper.R")
source("../useful_dplyr.R")
```

Preliminary CI analysis
---

```{r}
ms <- seq(.1,.9,.1)
ns <- c(10,20,50,100)

n.samps <- 10000
d <- data.frame()

for (m in ms) {
  for (n in ns) {
    d <- rbind_list(d, 
                   data.frame(m = m,                            
                              n = n,
                              p = rbinom(n.samps, n, m)))  
    }
  }
  
ms <- d %>% 
  group_by(m,n) %>%
  summarise(em = mean(p/n),
            ymin = quantile(p/n, .025),
            ymax = quantile(p/n, .975))

qplot(x=m, y=em, ymin=ymin, ymax=ymax, col=factor(n), 
      position=position_dodge(.03), group=factor(n),
      geom=c("line","linerange"), data=ms) + facet_wrap(~n)
```
  

Dependent Variables
----

This reads in a mess of files with different measures. 

Note that I excluded a number of files in a directory called "unused."

```{r}
files <- dir("../../data/1-prelims/dv/")
d <- data.frame()
measures <- c("forced_choice", "betting", "likert")

for (t in measures) {
  fs <- files[grepl(t, files)]
  
  for (f in fs) {
    print(f)
    d.new <- read.turk(paste("../../data/1-prelims/dv/",f, sep=""))
    d.new$dataset <- f
    d <- rbind_list(d, d.new)
  }
}

d <- d %>% mutate(response.cond = factor(measures[d$response.cond + 1]))
```

Counts and exclusions.

```{r}
d %>% group_by(response.cond) %>%
  summarise(n=length(workerid))

d %>% group_by(response.cond,item) %>%
  summarise(n=length(workerid))


dc <- d %>% filter(mc.targ == "2", 
                   mc.dist == "1", 
                   mc.name == "TRUE", 
                   duplicated(workerid) == FALSE)

dc %>% group_by(response.cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Note, there is a reversal of the terms "foil" and "distractor" between the likert and the betting conditions here. I've renamed.

```{r}
d.fc <- dc %>% filter(response.cond == "forced_choice") %>%
  group_by(item) %>%
  summarise(pragmatic = mean(choice == "target"),             
            logical = mean(choice == "logical"),
            foil = mean(choice == "foil"),
            pragmatic.cih = ci.high(choice == "target"),
            pragmatic.cil = ci.low(choice == "target"),
            logical.cih = ci.high(choice == "logical"),
            logical.cil = ci.low(choice == "logical"),
            foil.cih = ci.high(choice == "foil" ),
            foil.cil = ci.low(choice == "foil"),
            n = length(workerid), 
            response.cond = response.cond[1])
  
d.likert <- dc %>% filter(response.cond == "likert") %>%
  group_by(item) %>%
  summarise(pragmatic = mean(targ.likert/7), 
            logical = mean(foil.likert)/7, 
            foil = mean(dist.likert)/7, 
            pragmatic.cih = ci.high(targ.likert)/7,
            pragmatic.cil = ci.low(targ.likert)/7,
            logical.cih = ci.high(foil.likert)/7,
            logical.cil = ci.low(foil.likert)/7,
            foil.cih = ci.high(dist.likert)/7,
            foil.cil = ci.low(dist.likert)/7,
            n = length(workerid), 
            response.cond = response.cond[1])

d.bet <- dc %>% filter(response.cond == "betting") %>%
  group_by(item) %>%
  summarise(pragmatic = mean(targ.bet)/100, 
            logical = mean(dist.bet)/100, 
            foil = mean(foil.bet)/100, 
            pragmatic.cih = ci.high(targ.bet)/100,
            pragmatic.cil = ci.low(targ.bet)/100,
            logical.cih = ci.high(dist.bet)/100,
            logical.cil = ci.low(dist.bet)/100,
            foil.cih = ci.high(foil.bet)/100,
            foil.cil = ci.low(foil.bet)/100,
            n = length(workerid),
            response.cond = response.cond[1])
```

Plot. 

```{r}
ms <- rbind_list(d.fc, d.likert, d.bet) %>% 
  gather(measure, value, pragmatic, logical, 
         foil, pragmatic.cil, logical.cil, 
         foil.cil, pragmatic.cih, logical.cih, foil.cih) %>%
  mutate(role = ifelse(grepl("cih",measure), "cih", 
                       ifelse(grepl("cil",measure), "cil", "mean")),
         measure = str_replace(measure,".ci[lh]","")) %>%
  spread(role, value)

qplot(measure, mean, geom=c("bar","linerange"), stat="identity",
      ymin=mean - cil, ymax=mean + cih, fill=measure,
      facets=response.cond~item, 
  data=ms) 
```

Exactly the same thing without the items.


```{r}
d.fc <- dc %>% filter(response.cond == "forced_choice") %>%
  summarise(pragmatic = mean(choice == "target"),             
            logical = mean(choice == "logical"),
            foil = mean(choice == "foil"),
            pragmatic.cih = ci.high(choice == "target"),
            pragmatic.cil = ci.low(choice == "target"),
            logical.cih = ci.high(choice == "logical"),
            logical.cil = ci.low(choice == "logical"),
            foil.cih = ci.high(choice == "foil" ),
            foil.cil = ci.low(choice == "foil"),
            n = length(workerid), 
            response.cond = response.cond[1])
  
d.likert <- dc %>% filter(response.cond == "likert") %>%
  summarise(pragmatic = mean(targ.likert/7), 
            logical = mean(foil.likert)/7, 
            foil = mean(dist.likert)/7, 
            pragmatic.cih = ci.high(targ.likert)/7,
            pragmatic.cil = ci.low(targ.likert)/7,
            logical.cih = ci.high(foil.likert)/7,
            logical.cil = ci.low(foil.likert)/7,
            foil.cih = ci.high(dist.likert)/7,
            foil.cil = ci.low(dist.likert)/7,
            n = length(workerid), 
            response.cond = response.cond[1])

d.bet <- dc %>% filter(response.cond == "betting") %>%
  summarise(pragmatic = mean(targ.bet)/100, 
            logical = mean(dist.bet)/100, 
            foil = mean(foil.bet)/100, 
            pragmatic.cih = ci.high(targ.bet)/100,
            pragmatic.cil = ci.low(targ.bet)/100,
            logical.cih = ci.high(dist.bet)/100,
            logical.cil = ci.low(dist.bet)/100,
            foil.cih = ci.high(foil.bet)/100,
            foil.cil = ci.low(foil.bet)/100,
            n = length(workerid),
            response.cond = response.cond[1])

ms <- rbind_list(d.fc, d.likert, d.bet) %>% 
  gather(measure, value, pragmatic, logical, 
         foil, pragmatic.cil, logical.cil, 
         foil.cil, pragmatic.cih, logical.cih, foil.cih) %>%
  mutate(role = ifelse(grepl("cih",measure), "cih", 
                       ifelse(grepl("cil",measure), "cil", "mean")),
         measure = str_replace(measure,".ci[lh]","")) %>%
  spread(role, value)

pdf("../../plots/1-prelims-dv.pdf", width=8, height=3.5)
qplot(measure, mean, geom=c("bar","linerange"), stat="identity",
      ymin=mean - cil, ymax=mean + cih, fill=measure,
      facets=.~response.cond, 
  data=ms) + 
  ylim(c(0,1)) + 
  ylab("Normalized measure mean") + 
  xlab("Target")
dev.off()
```

Analysis of "hedging" by choosing the same rating for pragmatic and logical. 

```{r}
dc %>% group_by(response.cond) %>%
  summarise(mean(targ.likert==foil.likert), # same dumb error with dist = foil
            mean(targ.bet == dist.bet))
```

Manipulation check
----

Files: 

* forced_choice_no_fam_6random_count_ALLS.csv
* forced_choice_no_fam_6random_NOcount_ALNC.csv

```{r}
d1 <- read.turk("../../data/1-prelims/manip/forced_choice_no_fam_6random_count_ALLS.tsv")
d2 <- read.turk("../../data/1-prelims/manip/forced_choice_no_fam_6random_NOcount_ALNC.tsv")
d1$cond <- "manip check"
d2$cond <- "no manip check"
d1$mc.targ <- as.numeric(d1$mc.targ)
d1$mc.dist <- as.numeric(d1$mc.dist)
d <- rbind_list(d1,d2)
```

Counts and exclusions

```{r}

d %>% group_by(cond,item) %>%
  summarise(n=length(workerid))

dc <- d %>% filter(mc.targ == 2 | mc.targ == -1, 
                   mc.dist == 1 | mc.dist == -1, 
                   mc.name == "TRUE", 
                   duplicated(workerid) == FALSE)

d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now average and plot with item. 

```{r}
d.fc <- dc %>% group_by(cond,item) %>%
  summarise(pragmatic = mean(choice == "target"),             
            logical = mean(choice == "logical"),
            foil = mean(choice == "foil"),
            pragmatic.cih = ci.high(choice == "target"),
            pragmatic.cil = ci.low(choice == "target"),
            logical.cih = ci.high(choice == "logical"),
            logical.cil = ci.low(choice == "logical"),
            foil.cih = ci.high(choice == "foil" ),
            foil.cil = ci.low(choice == "foil"),
            n = length(workerid))
  
ms <- d.fc %>%
  gather(measure, value, pragmatic, logical, 
         foil, pragmatic.cil, logical.cil, 
         foil.cil, pragmatic.cih, logical.cih, foil.cih) %>%
  mutate(role = ifelse(grepl("cih",measure), "cih", 
                       ifelse(grepl("cil",measure), "cil", "mean")),
         measure = str_replace(measure,".ci[lh]","")) %>%
  spread(role, value)

qplot(measure, mean, geom=c("bar","linerange"), stat="identity",
      ymin=mean - cil, ymax=mean + cih, fill=measure,
      facets=cond~item, 
  data=ms) + 
  ylim(c(0,1)) + 
  ylab("Mean") + 
  xlab("Target")
```

And without item.

```{r}
d.fc <- dc %>% group_by(cond) %>%
  summarise(pragmatic = mean(choice == "target"),             
            logical = mean(choice == "logical"),
            foil = mean(choice == "foil"),
            pragmatic.cih = ci.high(choice == "target"),
            pragmatic.cil = ci.low(choice == "target"),
            logical.cih = ci.high(choice == "logical"),
            logical.cil = ci.low(choice == "logical"),
            foil.cih = ci.high(choice == "foil" ),
            foil.cil = ci.low(choice == "foil"),
            n = length(workerid))
  
ms <- d.fc %>%
  gather(measure, value, pragmatic, logical, 
         foil, pragmatic.cil, logical.cil, 
         foil.cil, pragmatic.cih, logical.cih, foil.cih) %>%
  mutate(role = ifelse(grepl("cih",measure), "cih", 
                       ifelse(grepl("cil",measure), "cil", "mean")),
         measure = str_replace(measure,".ci[lh]","")) %>%
  spread(role, value)

pdf("../../plots/1-prelims-manip.pdf", width=6, height=3)
qplot(measure, mean, geom=c("bar","linerange"), stat="identity",
      ymin=mean - cil, ymax=mean + cih, fill=measure,
      facets=.~cond, 
  data=ms) + 
  ylim(c(0,1)) + 
  ylab("Mean") + 
  xlab("Target")
dev.off()
```

Stats.

```{r}

ms <- dc %>% group_by(cond) %>%
  summarise(pragmatic = sum(choice == "target"),             
            logical = sum(choice == "logical"),
            foil = sum(choice == "foil"))

chisq.test(as.matrix(ms[,2:4]))
```


Linguistic frame
----

Goal is to find out whether the "bob can say one word: glasses" is different from "bob says 'my friend has glasses'" frames.

Files: 
* forced_choice_no_fam_6random_count_baseratesmy_14jan2015_BASERATES

Ling cond = 1 ->
Ling cond = 13 ->
```{r}
d <- read.turk("../../data/1-prelims/linguistic_framing/forced_choice_no_fam_6random_count_baseratesmy_14jan2015_BASERATES.tsv")

d$ling.cond <- factor(d$ling.cond, 
                      levels = c(1, 13), 
                      labels = c("one word","friend has"))
```

Counts and exclusions

```{r}
d %>% group_by(ling.cond) %>%
  summarise(n=length(workerid))

dc <- d %>% filter(mc.targ == "2", 
                   mc.dist == "1", 
                   mc.name == "TRUE", 
                   duplicated(workerid) == FALSE)

d %>% group_by(ling.cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(ling.cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now average and plot with item. 

```{r}
d.fc <- dc %>% group_by(ling.cond) %>%
  summarise(pragmatic = mean(choice == "target"),             
            logical = mean(choice == "logical"),
            foil = mean(choice == "foil"),
            pragmatic.cih = ci.high(choice == "target"),
            pragmatic.cil = ci.low(choice == "target"),
            logical.cih = ci.high(choice == "logical"),
            logical.cil = ci.low(choice == "logical"),
            foil.cih = ci.high(choice == "foil" ),
            foil.cil = ci.low(choice == "foil"),
            n = length(workerid))
  
ms <- d.fc %>%
  gather(measure, value, pragmatic, logical, 
         foil, pragmatic.cil, logical.cil, 
         foil.cil, pragmatic.cih, logical.cih, foil.cih) %>%
  mutate(role = ifelse(grepl("cih",measure), "cih", 
                       ifelse(grepl("cil",measure), "cil", "mean")),
         measure = str_replace(measure,".ci[lh]","")) %>%
  spread(role, value)

pdf("../../plots/1-prelims-lingframe.pdf", width=6, height=3)
qplot(measure, mean, geom=c("bar","linerange"), stat="identity",
      ymin=mean - cil, ymax=mean + cih, fill=measure,
      facets=.~ling.cond, 
  data=ms) + 
  ylim(c(0,1)) + 
  ylab("Mean") + 
  xlab("Target")
dev.off()
```

Stats.

```{r}

ms <- dc %>% group_by(ling.cond) %>%
  summarise(pragmatic = sum(choice == "target"),             
            logical = sum(choice == "logical"),
            foil = sum(choice == "foil"))

chisq.test(as.matrix(ms[,2:4]))
```