---
title: "Prior analysis"
author: "Mike Frank"
date: "November 5, 2014"
output: pdf_document
---
  
```{r}
rm(list=ls())
source("../helper.R")
source("../useful_dplyr.R")
```

Does it matter how we measure the prior? 
----

```{r}
d <- read.turk("../../data/2-prior/measurement/forced_choice_no_fam_6random_count_onewordmumble_21jan2015_WORDMUMBLE.tsv")

d$cond <- factor(d$ques.cond)
levels(d$cond) <- c("mumble","action")
```

Counts and exclusions. Note that MANY workers in this experiment misinterpreted and counted the familiarization stimuli, so there are a LOT of exclusions (28.5%)

```{r}
dc <- d %>% filter(as.numeric(mc.targ) == 2,
                   as.numeric(mc.dist) == 1,
                   mc.name == "TRUE",
                   duplicated(workerid)==FALSE)

d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
library(binom)
ms <- dc %>% 
  group_by(cond, choice) %>%  
  summarise(n = n()) %>%
  group_by(cond) %>%
  mutate(prop = n / sum(n), 
         cil = binom.bayes(n, sum(n))$lower,
         cih = binom.bayes(n, sum(n))$upper)  

pdf("../../plots/2-prior-frame.pdf", width=6, height=3.5)
qplot(choice, prop, geom=c("bar","linerange"), stat="identity",
      ymin=cil, ymax=cih, position=position_dodge(width=.9), 
      fill=factor(cond),
      data=ms) + 
  ylim(c(0,1)) + 
  ylab("Proportion correct") + 
  xlab("Base rate of target")
dev.off()
```

Models

```{r}
dc %>%  
  group_by(cond, choice) %>%
  summarise(n = n()) %>%
  spread(choice, n)
```

Stats

```{r}
library(binom)
ms <- dc %>% 
  group_by(cond, choice) %>%  
  summarise(n = n()) %>%
  spread(choice, n)

chisq <- chisq.test(as.matrix(ms[,2:4]))
chisq
```

Base rate manipulation
-----

Files:

* scale_6stimuli_yes_fam_oneword_25_february_FAMO.csv
* scale_6stimuli_yes_fam_oneword_25_february_FAMO2.csv
* scale_6stimuli_yes_fam_mumblemumble_26_february_FMMM.csv


```{r}
d1 <- read.turk("../../data/2-prior/baserates/scale_6stimuli_yes_fam_oneword_25_february_FAMO.tsv")
d2 <- read.turk("../../data/2-prior/baserates/scale_6stimuli_yes_fam_oneword_25_february_FAMO2.tsv")
d1$cond <- "inference"
d2$cond <- "inference"

d3 <-  read.turk("../../data/2-prior/baserates/scale_6stimuli_yes_fam_mumblemumble_26_february_FMMM.tsv")
d3$cond <- "prior"

d <- rbind_list(d1,d2,d3) 

d <- d %>% mutate(baserate = c(1/9,3/9,5/9,7/9)[familiarization + 1])
```

Counts and exclusions. Note that MANY workers in this experiment misinterpreted and counted the familiarization stimuli, so there are a LOT of exclusions (28.5%)

```{r}
d %>% group_by(cond, baserate) %>%
  summarise(n=length(workerid))

dc <- d %>% filter(as.numeric(mc.targ) == 2,
                   as.numeric(mc.dist) == 1,
                   mc.name == "TRUE", 
                   duplicated(workerid) == FALSE)

dc %>% group_by(cond,baserate) %>%
  summarise(n=length(workerid))


d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  mutate(cond = factor(cond)) %>%
  group_by(cond, baserate) %>%
  summarise(n = n(), 
            correct = mean(choice == "target"),             
            cih = ci.high(choice == "target"),
            cil = ci.low(choice == "target"))

pdf("../../plots/2-prior-baserates.pdf", width=6, height=3.5)
qplot(baserate, correct, geom=c("line","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, col=cond,
      data=ms) + 
  ylim(c(0,1)) + 
  xlim(c(0,1)) +
  ylab("Proportion correct") + 
  xlab("Base rate of target")
dev.off()
```

Stats.

```{r}
d$correct <- d$choice=="target"
dc$correct <- dc$choice=="target"
dc$cond <- factor(dc$cond, levels = c("inference","prior"))
summary(glm(correct ~ baserate * cond, data=dc))

summary(glm(correct ~ baserate, data=filter(dc, cond=="inference")))
```

Output for models.

```{r}
dc %>%  
  group_by(cond, baserate, choice) %>%
  summarise(n = n()) %>%
  spread(choice, n) 
```

Linguistic Manipulation
----

Files:

"favorite":
* forced_choice_no_fam_friends_30_november.csv
* forced_choice_no_fam_boat_1_december_XYZQ.csv
* forced_choice_no_fam_pizza_30_november.csv
* forced_choice_no_fam_snowman_30_november.csv

The "least favorite" condition is computed from the file:
* forced_choice_no_fam_4random_count_12_january_least_LEAS.csv

prior
* scale_6stimuli_no_fam_prior_5_april_PRIOLF.csv

```{r}
d1a <- read.turk("../../data/2-prior/language/forced_choice_no_fam_friends_30_november.tsv")
d1b <- read.turk("../../data/2-prior/language/forced_choice_no_fam_boat_1_december_XYZQ_incomplete.tsv")
d1c <- read.turk("../../data/2-prior/language/forced_choice_no_fam_pizza_30_november.tsv")
d1d <- read.turk("../../data/2-prior/language/forced_choice_no_fam_snowman_30_november.tsv")
d2 <- read.turk("../../data/2-prior/language/forced_choice_no_fam_4random_count_12_january_least_LEAS.tsv")
d3 <- read.turk("../../data/2-prior/language/scale_6stimuli_no_fam_prior_5_april_PRIOLF.tsv")

d <- rbind_list(d1a,d1b,d1c,d1d,d2,d3) 
d$cond <- factor(d$ling.cond)
levels(d$cond) <- c("favorite","least favorite","favorite prior","least favorite prior")
```

Counts and exclusions.

```{r}
dc <- d %>% filter(as.numeric(mc.targ) == 2,
                   as.numeric(mc.dist) == 1,
                   mc.name == "TRUE")

d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  group_by(cond) %>%
  summarise(correct = mean(choice == "target"),
            foil = mean(choice == "logical"), 
            dist = mean(choice == "foil"),
            cih = ci.high(choice == "target"),
            cil = ci.low(choice == "target"))

pdf("../../plots/2-prior-valence.pdf", width=6, height=3.5)
qplot(cond, correct, geom=c("bar","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, fill=factor(cond),
      data=filter(ms, !grepl("prior",cond))) + 
  ylim(c(0,1)) + 
  ylab("Proportion correct") + 
  xlab("Base rate of target")
dev.off()
```

Output for models.

```{r}
dc %>%  
  group_by(cond, choice) %>%
  summarise(n = n()) %>%
  spread(choice, n)
```


Perceptual salience (color) manipulation
----

Files:

* forced_choice_no_fam_6random_2count_oneword_4mar2015_COLORBASE
* forced_choice_no_fam_6random_2count_oneword_23feb2015_COLORSALIENCE

```{r}
d1 <- read.turk("../../data/2-prior/color/forced_choice_no_fam_6random_2count_oneword_4mar2015_COLORBASE.tsv")
d2 <- read.turk("../../data/2-prior/color/forced_choice_no_fam_6random_2count_oneword_23feb2015_COLORSALIENCE.tsv")

d <- rbind_list(d1,d2) 
d$cond <- factor(d$ling.cond)
levels(d$cond) <- c("inference","prior")
```

Counts and exclusions.

```{r}
dc <- d %>% filter(as.numeric(mc.targ) == 2,
                   as.numeric(mc.dist) == 1,
                   mc.name == "TRUE")

d %>% group_by(cond) %>%
  summarise(n=length(workerid))

dc %>% group_by(cond) %>%
  summarise(n=length(workerid))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Now get averages and CIs.

```{r}
ms <- dc %>% 
  group_by(cond, referent_with_color) %>%
  summarise(correct = mean(choice == "target"),
            foil = mean(choice == "logical"), 
            dist = mean(choice == "foil"),
            cih = ci.high(choice == "target"),
            cil = ci.low(choice == "target"))

pdf("../../plots/2-prior-color.pdf", width=6, height=3.5)
qplot(cond, correct, geom=c("bar","linerange"), stat="identity",
      ymin=correct - cil, ymax=correct + cih, 
      position=position_dodge(width=.9),
      fill=referent_with_color,
      data=filter(ms, !grepl("prior",cond))) + 
  ylim(c(0,1)) + 
  ylab("Proportion correct") + 
  xlab("Referent displayed in color")
dev.off()
```

Output for models.

```{r}
dc %>%  
  group_by(cond, referent_with_color, choice) %>%
  summarise(n = n()) %>%
  spread(choice, n)
```