---
title: "seq2_analysis"
author: "Avery Katko"
date: "August 7, 2014"
output: html_document
---

```{r}
rm(list=ls())
library(ggplot2)
library(reshape2)
library(plyr)
library(bootstrap)
#source("useful.R")
setwd("~/github/local/ibr_pragmods")
#source("tests.R")
setwd("~/github/local/pragmods")
d <- read.csv("seq_data/pragmods_seq2.anondata.csv")
#head(d)
```

Exclude participants that either failed manipulation check or were rejected.

```{r}
exclude <- d$assignmentstatus == "Rejected" |
  d$Answer.name_check_correct == "\"FALSE\""
sum(exclude)
mean(exclude)

d <- subset(d, exclude == FALSE)

d$Answer.choice_correct_1 <- factor(as.logical(d$Answer.choice_correct_1))
d$Answer.choice_correct_2 <- factor(as.logical(d$Answer.choice_correct_2))
d$Answer.choice_correct_3 <- factor(as.logical(d$Answer.choice_correct_3))
```

Restructure data to have trial variable. (working around mturk data submission limitations; can't safely submit arrays, so we have to use separate variables for each trial)

```{r}
d$level_1 <- factor(ifelse(d$Answer.sequence_condition == "\"0w1w2w\"",0,2))
d$level_2 <- factor(rep(1,nrow(d)))
d$level_3 <- factor(ifelse(d$Answer.sequence_condition == "\"0w1w2w\"",2,0))

trial.df <- function(tn){
  df <- data.frame(id = d$workerid,
                   seqCond = d$Answer.sequence_condition,
                   trial = factor(rep(tn,nrow(d))),
                   level = d[sprintf("level_%d",tn)],
                   item = d[sprintf("Answer.item_%d",tn)],
                   targetProp = d[sprintf("Answer.target_prop_%d",tn)],
                   distractorProp = d[sprintf("Answer.distractor_prop_%d",tn)],
                   targetPosition = d[sprintf("Answer.target_position_%d",tn)],
                   distractorPosition = d[sprintf("Answer.distractor_position_%d",tn)],
                   choice = d[sprintf("Answer.choice_%d",tn)],
                   choiceCorrect = d[sprintf("Answer.choice_correct_%d",tn)])
  names(df) <- c("id","seqCond","trial","level","item","targetProp","distractorProp",
                 "targetPosition","distractorPosition","choice","choiceCorrect")
  return(df)
}

d2 <- rbind(trial.df(1),trial.df(2),trial.df(3))
d2$level <- ordered(d2$level, levels = c("0","1","2"))
summary(d2)
```

```{r}
#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}

ms <- aggregate(choiceCorrect ~ seqCond + trial + level,data = d2,l.mean)
ms$cil <- aggregate(choiceCorrect ~ seqCond + trial + level, data = d2, l.ci.low)$choiceCorrect
ms$cih <- aggregate(choiceCorrect ~ seqCond + trial + level, data = d2, l.ci.high)$choiceCorrect

#colorblind-friendly color palettes
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Compare performance on trials, in chronological order; facet by ordering condition.

```{r}
ggplot(data = ms, aes(x = trial, y = choiceCorrect, fill = level)) +
  geom_bar(stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = choiceCorrect - cil, ymax = choiceCorrect + cih), width = 0.2) +
  facet_grid(. ~ seqCond) + 
  theme_bw() +
  scale_fill_manual(values=cbPalette)
```

Compare performance in each condition for each inference level

```{r}
ggplot(data = ms, aes(x = seqCond, y = choiceCorrect, fill = seqCond)) +
  geom_bar(stat = "identity", color = "black") +
  geom_errorbar(aes(ymin = choiceCorrect - cil, ymax = choiceCorrect + cih), width = 0.2) +
  facet_grid(. ~ level) +
  theme_bw() +
  scale_fill_manual(values=cbPalette)
```

```{r}
setwd("~/github/local/ibr_pragmods")
source("tests.R")

LS(linear)
LSLS(linear)

# four models
# 1. don't update matrix
# 2. don't reuse word
# 3. don't reuse object
# 4. don't reuse either

#NOTE: just changed all as.numeric parts to remove +1's

max.col <- function(row){
  max.idx = 1
  for(i in 1:ncol(row)){
    if(row[i] > row[max.idx]){
      max.idx = i
    }
  }
  return(max.idx)
}
target.idx <- function(l){ # return col.# w/ target ref for level l
  return(c(3,1,2)[as.numeric(l)])
}
choice.idx <- function(choice,level) # return col# w/ chosen ref
{
  tbl = data.frame(target=c(0,1,2),logical=c(1,2,0),foil=c(2,0,1))
  return(target.idx(tbl[as.numeric(level),choice]+1))
}

response.probs <- data.frame()
for (p in d2$id) {
  target.mat <- linear
  eref.mat <- linear
  lex.mat <- linear
  never.same.mat <- linear
  #eboth.mat <- linear
  particip.data <- subset(d2,id==p)
  for (tn in 1:3) {
    cur.df <- subset(particip.data,trial==tn)
    word.row <- c(1,2,3)[as.numeric(cur.df$level)]
    target.col <- target.idx(cur.df$level) # c(3,1,2)[cur.df$level+1]
    choice.col <- choice.idx(cur.df$choice,cur.df$level)
    response.probs <- rbind.fill(response.probs,
                                 data.frame(particip=p,
                                            trial=tn,
                                            condition=cur.df$seqCond,
                                            level=cur.df$level,
                                            human.choice=cur.df$choice,
                                            rp.target.L0=L0(target.mat)[word.row,target.col],
                                            rp.target.LS=LS(target.mat)[word.row,target.col],
                                            
                                            rp.eref.target=L0(eref.mat)[word.row,target.col],
                                            rp.lex.target=L0(lex.mat)[word.row,target.col],
                                            rp.never.same.target=L0(never.same.mat)[word.row,target.col],
                                            rp.choice.L0=L0(target.mat)[word.row,choice.col],
                                            rp.choice.LS=LS(target.mat)[word.row,choice.col],
                                            
                                            rp.eref.choice=L0(eref.mat)[word.row,choice.col],
                                            rp.lex.choice=L0(lex.mat)[word.row,choice.col],
                                            rp.never.same.choice=L0(never.same.mat)[word.row,choice.col]
                                            #more...
                                            ))

    # evolve matrix according to some rule
    eref.mat[choice.idx(cur.df$choice,cur.df$level),] <- 0 # don't reuse referent
    
    # lexicalize word as referring to chosen ref
    lex.mat[,word.row] <- 0
    lex.mat[cur.df$choice,word.row] <- 1
    
    # don't reuse word-referent pair
    never.same.mat[cur.df$choice,word.row] <- 0
    
    #pe.word.mat[target[blah],] <- ... # don't reuse word
    #pe.both.mat[...] <- ... # don't reuse either
  }# for tn
}# for p

```
