---
title: Overspecification: level 1, virtual keyboard entry
output: html_document
---

##Basic information
Participants: 150
Dates: ???
Description of study: Participants encounter a level 1 reference game paradigm. They are asked to describe any of the three possible referents by clicking on keys using an on-screen virtual keyboard (from http://mottie.github.io/Keyboard/basic.html).
Hypothesis: The virtual keyboard is cumbersome and time-consuming; thus, the cost of expression is fairly high. Participants should overspecify less than in the other conditions.

---

##Data preprocessing

Open csv file.

```{r}
d3 <- read.csv("~/Documents/CSLI/pragmods_paul/experiments/pragmods_overspec_virtual.results.csv")
```

Exclude participants who answered incorrectly and those who failed the name check.

```{r}
exclude <- d3$Answer.name_check_correct == "\"FALSE\"" | d3$Answer.overspec == "NA"
d3 <- subset(d3, exclude == FALSE)
```

Aggregate the data into a table that shows instances of overspecification by condition.

```{r}
library(plyr)
overspec3 <- ddply(d3, .(Answer.features_in_referent_to_describe), summarise,
                   no = sum(Answer.overspec==0),
                   yes = sum(Answer.overspec==1),
                   no.prop = mean(Answer.overspec==0),
                   yes.prop = mean(Answer.overspec==1))
```

---
##Statistical Analyses

Add error bars to graphs:

```{r}
#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
library(bootstrap)
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}

d3ms <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = d3, l.mean)
d3ms$cil <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = d3, l.ci.low)$Answer.overspec
d3ms$cih <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = d3, l.ci.high)$Answer.overspec
```

Run a chi-squared test:

```{r}
chisq.test(overspec3[,c("no","yes")]) 
#    X-squared = 27.1589, df = 2, p-value = 1.266e-06
```

##Visualization
Convert the data (with error bars) into a bar graph:

```{r}
library(ggplot2)
qplot(Answer.features_in_referent_to_describe,
      Answer.overspec,
      data=d3ms,
      geom="bar",
      stat="identity",
      position="dodge",
      fill="red",
      xlab="Features in Referent",
      ylab="Proportion of Overspecification") +
      geom_errorbar(aes(ymin=Answer.overspec - cil, ymax = Answer.overspec + cih), width = 0.2) +
      ylim(c(0,1)) +
      theme(legend.position="none")
```