---
title: Overspecification: level 1, text entry
output: html_document
---

##Basic information
Participants: 150
Dates: ???
Description of study: Participants encounter a level 1 reference game paradigm. They are asked to describe any of the three possible referents by typing a description into a box.
Hypothesis: Given that the cost of expression is relatively low (i.e., typing does not require much effort), participants will, for the sake of clarity, overspecify to avoid potentail ambiguity caused by making an implicature.

---

##Data preprocessing

Open csv file.

```{r}
d1 <- read.csv("~/Documents/CSLI/pragmods_paul/experiments/pragmods_overspec_baseline.results.csv")
```

Exclude participants that answered incorrectly or failed to follow instructions. (In the free-response condition, this must be coded manually.)

```{r}
exclude <- d1$Answer.overspec == "NA"
d1 <- subset(d1, exclude == FALSE)
```

Aggregate the data into a table that shows instances of overspecification by condition.

```{r}
library(plyr)
overspec1 <- ddply(d1, .(Answer.features_in_referent_to_describe), summarise,
                  no = sum(Answer.overspec==0),
                  yes = sum(Answer.overspec==1),
                  no.prop = mean(Answer.overspec==0),
                  yes.prop = mean(Answer.overspec==1),
                  type = ("text"))
```

---
##Statistical Analyses

Add error bars to graphs:

```{r}
#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
library(bootstrap)
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}

d1ms <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = d1, l.mean)
d1ms$cil <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = d1, l.ci.low)$Answer.overspec
d1ms$cih <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = d1, l.ci.high)$Answer.overspec
```

Run a chi-squared test:

```{r}
chisq.test(overspec1[,c("no","yes")]) 
#    X-squared = 27.1589, df = 2, p-value = 1.266e-06
```

##Visualization
Convert the data (with error bars) into a bar graph:

```{r}
library(ggplot2)
qplot(Answer.features_in_referent_to_describe,
      Answer.overspec,
      data=d1ms,
      geom="bar",
      stat="identity",
      position="dodge",
      fill="red",
      xlab="Features in Referent",
      ylab="Proportion of Overspecification") +
      geom_errorbar(aes(ymin=Answer.overspec - cil, ymax = Answer.overspec + cih), width = 0.2) +
      ylim(c(0,1)) +    
      theme(legend.position="none")
```