---
title: Overspecification--sequence aggregation, level 2
output: html_document
---

##Basic Information
Participants: 450
Dates: ???
Description of study: Exactly the same as the level 1 sequence experiment, but with level 2 implicatures. 
Hypothesis: Participants may still struggle with level 2 implicatures, as has been the case in the literature.

---
##Data preprocessing
First, load all of the datasets.

```{r}
s1 <- read.csv("~/Documents/CSLI/pragmods_paul/experiments/pragmods_overspec_seq_basic.results.csv")
s2 <- read.csv("~/Documents/CSLI/pragmods_paul/experiments/pragmods_overspec_seq_checkbox.results.csv")
s3 <- read.csv("~/Documents/CSLI/pragmods_paul/experiments/pragmods_overspec_seq.results.csv")
```

Then, exclude the relevant cases from each of them:

```{r}
exclude <- s4$Answer.overspec == "NA"
s1 <- subset(s1, exclude == FALSE)

exclude <- s5$Answer.name_check_correct == "\"FALSE\"" | s5$Answer.overspec == "NA"
s2 <- subset(s2, exclude == FALSE)

exclude <- s6$Answer.overspec == "NA"
s3 <- subset(s3, exclude == FALSE)
```

Create tables for each dataset:

```{r}
library(plyr)

overspec1seq <- ddply(s1, .(Answer.features_in_referent_to_describe), summarise,
                  no = sum(Answer.overspec==0),
                  yes = sum(Answer.overspec==1),
                  no.prop = mean(Answer.overspec==0),
                  yes.prop = mean(Answer.overspec==1),
                  type = ("text"))

overspec2seq <- ddply(s2, .(Answer.features_in_referent_to_describe), summarise,
                   no = sum(Answer.overspec==0),
                   yes = sum(Answer.overspec==1),
                   no.prop = mean(Answer.overspec==0),
                   yes.prop = mean(Answer.overspec==1),
                   type = ("checkbox"))

overspec3seq <- ddply(s3, .(Answer.features_in_referent_to_describe), summarise,
                  no = sum(Answer.overspec==0),
                  yes = sum(Answer.overspec==1),
                  no.prop = mean(Answer.overspec==0),
                  yes.prop = mean(Answer.overspec==1),
                  type = ("virtual keyboard"))
```

Aggregate all of these into a single table:

```{r}
level2seq <- rbind(overspec1seq, overspec2seq, overspec3seq)
```

We're also interested if people made the correct inference in the sequence condition. Create tables for each experiment:

```{r}
targetcorrect1 <- ddply(s1, .(Answer.overspec), summarise,
                        no.prop = mean(Answer.targetcorrect==0),
                        yes.prop = mean(Answer.targetcorrect==1),
                        type = ("text"))

targetcorrect2 <- ddply(s2, .(Answer.overspec), summarise,
                        no.prop = mean(Answer.targetcorrect==0),
                        yes.prop = mean(Answer.targetcorrect==1),
                        type = ("checkbox"))

targetcorrect3 <- ddply(s3, .(Answer.overspec), summarise,
                        no.prop = mean(Answer.targetcorrect==0),
                        yes.prop = mean(Answer.targetcorrect==1),
                        type = ("virtual keyboard"))
```

And combine these:

```{r}
targetcorrectlvl2 <- rbind(targetcorrect1, targetcorrect2, targetcorrect3)
```

The above table shows us the percent of correct inferences based on whether or not participants overspecified. The next table will show this by input type:

```{r}
level2target <- ddply(targetcorrectlvl2, .(type), summarise,
                      correct=mean(yes.prop))
```

---
##Statistical Analyses

Add error bars to the data on overspecification by condition:

```{r}
library(bootstrap)
#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}

s1ms <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s1, l.mean)
s1ms$cil <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s1, l.ci.low)$Answer.overspec
s1ms$cih <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s1, l.ci.high)$Answer.overspec

s2ms <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s2, l.mean)
s2ms$cil <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s2, l.ci.low)$Answer.overspec
s2ms$cih <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s2, l.ci.high)$Answer.overspec

s3ms <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s3, l.mean)
s3ms$cil <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s3, l.ci.low)$Answer.overspec
s3ms$cih <- aggregate(Answer.overspec ~ Answer.features_in_referent_to_describe + Experiment.type, data = s3, l.ci.high)$Answer.overspec
```

```{r}
seqms2 <- rbind(s1ms, s2ms, s3ms)
```

And add error bars to the data on the percent of correct inferences:

```{r}
#statistics for boolean factors; copied from useful.R, with a slightly different mean function to work with the choiceCorrect factor
l.mean <- function(...){mean(as.logical(...))}
l.theta <- function(x,xdata,na.rm=T) {l.mean(xdata[x],na.rm=na.rm)}
l.ci.low <- function(x,na.rm=T) {
  l.mean(x,na.rm=na.rm) - quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.025,na.rm=na.rm)}
l.ci.high <- function(x,na.rm=T) {
  quantile(bootstrap(1:length(x),1000,l.theta,x,na.rm=na.rm)$thetastar,.975,na.rm=na.rm) - l.mean(x,na.rm=na.rm)}

s1cms <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s1, l.mean)
s1cms$cil <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s1, l.ci.low)$Answer.targetcorrect
s1cms$cih <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s1, l.ci.high)$Answer.targetcorrect

s2cms <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s2, l.mean)
s2cms$cil <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s2, l.ci.low)$Answer.targetcorrect
s2cms$cih <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s2, l.ci.high)$Answer.targetcorrect

s3cms <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s3, l.mean)
s3cms$cil <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s3, l.ci.low)$Answer.targetcorrect
s3cms$cih <- aggregate(Answer.targetcorrect ~ Answer.overspec + Experiment.type, data = s3, l.ci.high)$Answer.targetcorrect
```

Combine these:

```{r}
seqcms2 <- rbind(s1cms, s2cms, s3cms)
```

---
##Visualization
Convert the data (with error bars) into a bar graph:

```{r}
library(ggplot2)
qplot(Answer.features_in_referent_to_describe,
       Answer.overspec,
       data=seqms2,
       geom="bar",
       stat="identity",
       position="dodge",
       fill=factor(Experiment.type),
       xlab="Features in Referent",
       ylab="Proportion of Overspecification") +
       geom_errorbar(aes(ymin=Answer.overspec - cil, ymax = Answer.overspec + cih), width=0.2, position=position_dodge(width=.9)) +
       ylim(c(0,1)) +
       scale_fill_discrete(name="Experiment Type")
```

```{r}
labelx = c("No", "Yes")

qplot(factor(Answer.overspec),
       Answer.targetcorrect,
       data=seqcms2,
       geom="bar",
       stat="identity",
       position="dodge",
       fill=factor(Experiment.type),
       xlab="Overspecification",
       ylab="Proportion of Correct Responses") +
       geom_errorbar(aes(ymin=Answer.targetcorrect - cil, ymax = Answer.targetcorrect + cih), width=0.2, position=position_dodge(width=.9)) +
       ylim(c(0,1)) +
       scale_fill_discrete(name="Experiment Type") +
       scale_x_discrete(labels=labelx)
```
