---
title: "Speakers Analysis"
author: "Paul Mains & Mike Frank"
date: "November 13th, 2014"
output: pdf_document
---

Production effects
----

```{r}
setwd("~/Projects/Pragmatics/pragmods/")
rm(list=ls())
source("analysis/helper.R")
source("analysis/useful_dplyr.R")
```

Level 1
---

Read data.

```{r}
d1 <- read.turk("data/6-speakers/pragmods_overspec_baseline.results.csv")
d1$cond <- "text"
d1$workerid <- as.character(d1$workerid)
d2 <- read.turk("data/6-speakers/pragmods_overspec_checkbox.results.csv")
d2$cond <- "checkbox"
d2$free_response <- as.character(d2$free_response)
d3 <- read.turk("data/6-speakers/pragmods_overspec_virtual.results.csv")
d3$cond <- "virtual keyboard"

d <- rbind_list(d1,d2,d3)
d <- d %>% rename(targ.features = features_in_referent_to_describe)
```

Counts and exclusions. Note that this experiment has no manipulation check (Must check whether it has a manipulation check at all!). 

```{r}
dc <- d %>% filter(mc.name == "TRUE"& !is.na(overspec))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Aggregate: 

```{r}
ms <- dc %>% 
  group_by(targ.features, cond) %>%
  summarise(m = mean(overspec),
            cil = ci.low(overspec),
            cih = ci.high(overspec),
            n = length(overspec))
```

Convert the data (with error bars) into a bar graph:

```{r}
pdf("plots/6-speakers-level1.pdf",width=8, height=4)
qplot(targ.features, m, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=m - cil, ymax=m + cih), 
                 position = position_dodge(width=.9)) + 
  xlab("Features in Referent") + 
  ylab("Proportion Overspecification") + 
  scale_fill_discrete(name="Experiment Type")
dev.off()
```

Level 1 Sequential
---

Now analyze the same paradigm with level 1 sequential judgments.

```{r}
d1 <- read.turk("data/6-speakers/pragmods_overspec_seq_baseline_lvl1.results.csv")
d1$cond <- "text"
d1$workerid <- as.character(d1$workerid)
d2 <- read.turk("data/6-speakers/pragmods_overspec_seq_checkbox_lvl1.results.csv")
d2$cond <- "checkbox"
d2$keyboard <- as.character(d2$keyboard)
d3 <- read.turk("data/6-speakers/pragmods_overspec_seq_virtual_lvl1.results.csv")
d3$cond <- "virtual keyboard"

d <- rbind_list(d1,d2,d3)
d <- d %>% rename(targ.features = features_in_referent_to_describe)
```

Counts and exclusions. Note that this experiment has no manipulation check (Must check whether it has a manipulation check at all!). 

```{r}
dc <- d %>% filter(mc.name == "TRUE"& !is.na(overspec))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Aggregate: 

```{r}
ms <- dc %>% 
  group_by(targ.features, cond) %>%
  summarise(m = mean(overspec),
            cil = ci.low(overspec),
            cih = ci.high(overspec),
            correct = mean(choice_2 == "target"),
            correct.cil = ci.low(choice_2 == "target"),
            correct.cih = ci.high(choice_2 == "target"),
            n = length(overspec))
```

Convert the data (with error bars) into a bar graph:

```{r}
# pdf("plots/6-speakers-level1seq.pdf",width=8, height=4)
qplot(targ.features, m, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=m - cil, ymax=m + cih), 
                 position = position_dodge(width=.9)) + 
  xlab("Features in Referent") + 
  ylab("Proportion Overspecification") + 
  scale_fill_discrete(name="Experiment Type")
# dev.off()
```

Look at inference data. 

```{r}
pdf("plots/6-speakers-level1seq-inferences.pdf",width=8, height=4)
qplot(targ.features, correct, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=correct - correct.cil, ymax=correct + correct.cih), 
                 position = position_dodge(width=.9)) + 
  xlab("Features in Referent") + 
  ylab("Proportion Correct") + 
  scale_fill_discrete(name="Experiment Type")
dev.off()
```

Split by whether you overspecified. Hard to interpret this. 

```{r}
ms <- dc %>% 
  group_by(targ.features, overspec, cond) %>%
  summarise(correct = mean(choice_2 == "target"),
            correct.cil = ci.low(choice_2 == "target"),
            correct.cih = ci.high(choice_2 == "target"),
            n = length(overspec))

qplot(targ.features, correct, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=correct - correct.cil, ymax=correct + correct.cih), 
                 position = position_dodge(width=.9)) + 
  facet_grid(.~overspec) +
  xlab("Features in Referent") + 
  ylab("Proportion Correct") + 
  scale_fill_discrete(name="Experiment Type")
# dev.off()
```


Level 2 Sequential
---

Now analyze the same paradigm with level 1 sequential judgments.

```{r}
d1 <- read.turk("data/6-speakers/pragmods_overspec_seq_baseline_lvl2.results.csv")
d1$cond <- "text"
d1$workerid <- as.character(d1$workerid)
d2 <- read.turk("data/6-speakers/pragmods_overspec_seq_checkbox_lvl2.results.csv")
d2$cond <- "checkbox"
d2$keyboard <- as.character(d2$keyboard)
d3 <- read.turk("data/6-speakers/pragmods_overspec_seq_virtual_lvl2.results.csv")
d3$cond <- "virtual keyboard"

d <- rbind_list(d1,d2,d3)
d <- d %>% rename(targ.features = features_in_referent_to_describe)
```

Counts and exclusions. Note that this experiment has no manipulation check (Must check whether it has a manipulation check at all!). 

```{r}
dc <- d %>% filter(mc.name == "TRUE"& !is.na(overspec))

d %>% summarise(n=length(workerid))
dc %>% summarise(n=length(workerid))
```

Aggregate: 

```{r}
ms <- dc %>% 
  group_by(targ.features, cond) %>%
  summarise(m = mean(overspec),
            cil = ci.low(overspec),
            cih = ci.high(overspec),
            correct = mean(choice_2 == "target"),
            correct.cil = ci.low(choice_2 == "target"),
            correct.cih = ci.high(choice_2 == "target"),
            n = length(overspec))
```

Convert the data (with error bars) into a bar graph:

```{r}
pdf("plots/6-speakers-level2seq.pdf",width=8, height=4)
qplot(targ.features, m, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=m - cil, ymax=m + cih), 
                 position = position_dodge(width=.9)) + 
  xlab("Features in Referent") + 
  ylab("Proportion Overspecification") + 
  scale_fill_discrete(name="Experiment Type")
dev.off()
```

Look at inference data. 

```{r}
pdf("plots/6-speakers-level2seq-inferences.pdf",width=8, height=4)
qplot(targ.features, correct, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=correct - correct.cil, ymax=correct + correct.cih), 
                 position = position_dodge(width=.9)) + 
  xlab("Features in Referent") + 
  ylab("Proportion Correct") + 
  scale_fill_discrete(name="Experiment Type")
dev.off()
```

Split by whether you overspecified. 

```{r}
ms <- dc %>% 
  group_by(targ.features, overspec, cond) %>%
  summarise(correct = mean(choice_2 == "target"),
            correct.cil = ci.low(choice_2 == "target"),
            correct.cih = ci.high(choice_2 == "target"),
            n = length(overspec))

qplot(targ.features, correct, fill=cond, 
      geom="bar", stat="identity", position="dodge",
      data=ms) + 
  ylim(c(0,1)) + 
  geom_linerange(aes(ymin=correct - correct.cil, ymax=correct + correct.cih), 
                 position = position_dodge(width=.9)) + 
  facet_grid(.~overspec) +
  xlab("Features in Referent") + 
  ylab("Proportion Correct") + 
  scale_fill_discrete(name="Experiment Type")
# dev.off()
```


