---
title: "Model Simulations"
author: "Ben Peloquin"
date: "April 7, 2016"
output: html_document
---

Prelim set-up
```{r}
rm(list = ls())
```

```{r}
source("matrices.R")
library(rrrsa)
library(dplyr)
library(tidyr)
library(ggplot2)
```

Generic helpers
```{r}
#####
##### normalizeBy()
##### -------------
##### normaze matrix by rows or cols, maintain naming
#####
normalizeBy <- function(m, rows = TRUE) {
  colNames <- colnames(m)
  rowNames <- rownames(m)
  normedM <- t(apply(m, MARGIN = ifelse(rows, 1, 2), rrrsa::rsa.normVec))
  colnames(normedM) <- colNames
  rownames(normedM) <- rowNames
  normedM
}

#####
##### inGlobalEnv()
##### -------------
##### boolean object presence in global env
#####
inGlobalEnv <- function(item) {
  item %in% ls(envir = .GlobalEnv)
}

#####
##### getLiteralSemantics()
##### ---------------------
##### literal semantics mapper between 
##### normalized matrices and dataframe
##### called in mutate() within dplyr chain
#####
getLiteralSemantics <- function(matrixName, object, query) {
  if (!(inGlobalEnv("simpleM") | inGlobalEnv("complexM") | inGlobalEnv("oddmanM") | inGlobalEnv("twinsM"))) {
    stop("Missing normalized matrices, please run data pre-processing block")
  }
  
  if (matrixName == "simple") {
    simpleM[as.character(object), as.character(query)]
  } else if (matrixName == "complex") {
    complexM[as.character(object), as.character(query)]
  } else if (matrixName == "oddman") {
    oddmanM[as.character(object), as.character(query)]
  } else if (matrixName == "twins") {
    twinsM[as.character(object), as.character(query)]
  } else {
    stop("Error in getLiteralSemantics()")
  }
}

#####
##### completeQueries()
##### ---------------------
##### add "query" words for each expt
##### this is necessary for running with rrrsa::runDf
#####
completeQueries <- function(d) {
  newD <- d
  
  currMatrix <- unique(as.character(d$matrix))
  
  
  ## meta-data
  allQueries <- c("glasses", "hat", "mustache")
  allObjects <- c("foil", "logical", "target")
  
  ## The current query
  currQuery <- unique(as.character(d$query))
  neededQueries <- setdiff(allQueries, currQuery)
  
  ## Add in new queries
  for (q in neededQueries) {
    df <- data.frame(cond = as.vector(d$cond),
                     expt = as.vector(d$expt),
                     matrix = as.vector(d$matrix),
                     prior = as.vector(d$prior),
                     query = rep(q, 3),
                     object = as.vector(d$object),
                     count = rep(NA, 3),
                     p = rep(NA, 3),
                     n = as.vector(d$n),
                     cil = rep(NA, 3), 
                     cih = rep(NA, 3),
                     priorType = as.vector(d$priorType),
                     priorValue = as.vector(d$priorValue),
                     grouper = as.vector(d$grouper))
    newD <- rbind(newD, df)
    if (currMatrix == "simple") return(newD)
  }
  newD
}
# undebug(completeQueries)
# debug(completeQueries)
# completeQueries(baserate_63)
```

Get the data
```{r}
## This is `d` df from line 128 in sims.Rmd
d <- read.csv("data/models.csv")
# View(d)
```

Data pre-processing
```{r}
## Subsetted dfs
# simpleD <- d %>%
#   filter(matrix == "simple")
# complexD <- d %>%
#   filter(matrix == "complex")
# oddmanD <- d %>%
#   filter(matrix == "oddman")
# twinsD <- d %>%
#   filter(matrix == "twins")

## Renamed, normalized matrices from matrices.R
simpleM <- normalizeBy(simple, rows = TRUE)
complexM <- normalizeBy(complex, rows = TRUE)
twinsM <- normalizeBy(twins, rows = TRUE)
oddmanM <- normalizeBy(oddman, rows = TRUE)
```

Focus on simple
```{r}
## Here are the sceneriors - sort by expt and n
## Now we can match the query (word), object (meaning) combinations to matrices
## This code populates a new literal listener column
# simpleD2 <- simpleD %>% 
#   arrange(expt, n) %>% 
#   gather(priorType, priorValue, c(foil, logical, target)) %>%
#   filter(object == priorType) %>%
#   rowwise %>%
#   mutate(speaker.p = simpleM[as.character(object), as.character(query)])
```

Add literal semantics information from matrices

KEEP OLD NOTE:: HERE'S A PROBLEM to work with rrrsa::runDf we need each matrix to include the literal semantics of all the queries (even if they weren't actually queried)
Look at group 'baserate-63': only 'glasses' is queried, but we need to add the literal semantics for 'hat' and 'mustache' as well.
Practice rsa run with one group
```{r}
str(d)

## Initial pre-processing before adding in new cols and then adding literal semantics
processedD <- d %>%
  ## Gather priors - we're only interested in prior for current object
  gather(priorType, priorValue, c(foil, logical, target)) %>%
  ## Filter out an mismatches between current object and priorType
  filter(object == priorType) %>%
  rowwise %>%
  ## Grouping variable concatenates experiment type and sample size (expt-n)
  mutate(grouper = paste0(as.character(expt), "-", as.character(n)))

fullData <- plyr::ddply(processedD, .variables = ("grouper"), .fun = completeQueries) %>%
  rowwise %>%
  ## Each row gets a unique literal semantics from getLiteraSemantics() helper
  mutate(speaker.p = getLiteralSemantics(matrix, query = query, object = object)) %>%
  arrange(expt, n)
```

Subset run
```{r}
baserate_63 <- fullData %>% filter(grouper == "baserate-63")
rrrsa::rsa.runDf(baserate_63,
                 quantityVarName = "object", semanticsVarName = "speaker.p",
                 itemVarName = "query", priorsVarName = "priorValue")
# undebug(rrrsa::rsa.runDf)
# debug(rrrsa::rsa.runDf)
```

Full simulation
```{r}
rsaRun <- plyr::ddply(fullData, .variables = c("grouper"), rsa.runDf,
            quantityVarName = "object", semanticsVarName = "speaker.p",
            itemVarName = "query", priorsVarName = "priorValue") %>%
  rowwise %>%
  mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"))
  
keepIndices <- c("keep", "throwout")
compareIndices  <- which(rsaRun$tuningData %in% keepIndices)
rsaRun %>%
  rowwise %>%
  mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"))
  rrrsa::rsa.tuneDepthAlpha(., quantityVarName = "object", semanticsVarName = "speaker.p",
            itemVarName = "query", priorsVarName = "priorValue", compareDataName = )
```

