---
title: "Model Simulations"
author: "Ben Peloquin"
date: "April 7, 2016"
output:
  html_document:
    toc: true
---

# Prelim set-up
```{r}
rm(list = ls())
```

```{r warning = FALSE, message = FALSE}
setwd('/Users/benpeloquin/Desktop/Projects/Pragmods/models/')
source("matrices.R")
source("agents.R")
library(rrrsa)
library(dplyr)
library(tidyr)
library(ggplot2)
library(parallel)
```

## Generic helpers
```{r}
#####
##### normalizeBy()
##### -------------
##### normaze matrix by rows or cols, maintain naming
#####
normalizeBy <- function(m, rows = TRUE) {
  colNames <- colnames(m)
  rowNames <- rownames(m)
  normedM <- apply(m, MARGIN = ifelse(rows, 1, 2), rrrsa::rsa.normVec)
  colnames(normedM) <- colNames
  rownames(normedM) <- rowNames
  normedM
}

#####
##### inGlobalEnv()
##### -------------
##### boolean object presence in global env
#####
inGlobalEnv <- function(item) {
  item %in% ls(envir = .GlobalEnv)
}

#####
##### getLiteralSemantics()
##### ---------------------
##### literal semantics mapper between 
##### normalized matrices and dataframe
##### called in mutate() within dplyr chain
#####
getLiteralSemantics <- function(matrixName, object, query) {
  if (!(inGlobalEnv("simpleM") | inGlobalEnv("complexM") | inGlobalEnv("oddmanM") | inGlobalEnv("twinsM"))) {
    stop("Missing normalized matrices, please run data pre-processing block")
  }
  
  if (matrixName == "simple") {
    simpleM[as.character(object), as.character(query)]
  } else if (matrixName == "complex") {
    complexM[as.character(object), as.character(query)]
  } else if (matrixName == "oddman") {
    oddmanM[as.character(object), as.character(query)]
  } else if (matrixName == "twins") {
    twinsM[as.character(object), as.character(query)]
  } else {
    stop("Error in getLiteralSemantics()")
  }
}

#####
##### completeQueries()
##### ---------------------
##### add "query" words for each expt
##### this is necessary for running with rrrsa::runDf
#####
completeQueries <- function(d) {
  ## store data
  newD <- d
  currMatrix <- unique(as.character(d$matrix))
  
  ## meta-data
  allQueries <- c("glasses", "hat", "mustache")
  allObjects <- c("foil", "logical", "target")
  
  ## The current query
  currQuery <- unique(as.character(d$query))
  neededQueries <- setdiff(allQueries, currQuery)
  
  ## Add in new queries
  for (q in neededQueries) {
    df <- data.frame(cond = as.vector(d$cond),
                     expt = as.vector(d$expt),
                     matrix = as.vector(d$matrix),
                     prior = as.vector(d$prior),
                     query = rep(q, 3),
                     object = as.vector(d$object),
                     count = rep(NA, 3),
                     p = rep(NA, 3),
                     n = as.vector(d$n),
                     cil = rep(NA, 3), 
                     cih = rep(NA, 3),
                     priorType = as.vector(d$priorType),
                     priorValue = as.vector(d$priorValue),
                     grouper = as.vector(d$grouper))
    newD <- rbind(newD, df)
    if (currMatrix == "simple") return(newD)
  }
  newD
}
# undebug(completeQueries)
# debug(completeQueries)
# completeQueries(baserate_63)

#####
##### convertListToDf()
##### -----------------
##### Convert a list where each element represents
##### data for a different grouping variable
##### useful with simulations run below
#####
convertListToDF <- function(li) {
  df <- data.frame()
  nItems <- seq(1, length(li))
  for (i in nItems) {
    df <- rbind(df, as.data.frame(li[[i]]))
  }
  df
}
```

## Read in data
```{r}
## This is `d` df from line 128 in sims.Rmd
d <- read.csv("data/models.csv")
# View(d)
```

## Matrices from matrices.R
```{r}
## Renamed, normalized matrices from matrices.R
simpleM <- normalizeBy(simple, rows = FALSE)
complexM <- normalizeBy(complex, rows = FALSE)
twinsM <- normalizeBy(twins, rows = FALSE)
oddmanM <- normalizeBy(oddman, rows = FALSE)
```

# Data pre-processing

NOTE:: To work with rrrsa::runDf we need each matrix to include the literal semantics of all the queries (even if they weren't actually queried)
Look at group 'baserate-63': only 'glasses' is queried, but we need to add the literal semantics for 'hat' and 'mustache' as well.
```{r}
## Initial pre-processing before adding in new cols and then adding literal semantics
processedD <- d %>%
  ## Gather priors - we're only interested in prior for current object
  gather(priorType, priorValue, c(foil, logical, target)) %>%
  ## Filter out any mismatches between current object and priorType
  filter(object == priorType) %>%
  rowwise %>%
  ## Grouping variable concatenates experiment type and sample size (expt-n)
  mutate(grouper = paste0(as.character(expt), "-", as.character(n)))

fullData <- plyr::ddply(processedD, .variables = ("grouper"), .fun = completeQueries) %>%
  rowwise %>%
  ## Each row gets a unique literal semantics from getLiteraSemantics() helper
  mutate(speaker.p = getLiteralSemantics(matrix, query = query, object = object)) %>%
  arrange(expt, n)
```

# Simulations WITH priors (recursive depth 0-5)

## Recursive depth sims
```{r}
depths <- seq(0, 5)
sims_prior_temp <- lapply(depths, function(depth) {
  plyr::ddply(fullData, .variables = c("grouper"), rsa.runDf,
            quantityVarName = "object", semanticsVarName = "speaker.p",
            itemVarName = "query", priorsVarName = "priorValue", depth = depth, usePriorEveryRecurse = FALSE) %>%
  rowwise %>%
  mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"),
         depth = depth) %>%
  filter(tuningData == "keep")
})
sims_prior <- convertListToDF(sims_prior_temp)
```

## Simulation plots

### Recursive depth 0-2
```{r}
sims_prior %>%
  filter(depth < 3) %>%
  ggplot(., aes(x = preds, y = p, col = expt, pch = object)) +
    geom_pointrange(aes(ymin = cil, ymax = cih)) + 
    xlim(c(0,1)) + ylim(c(0,1)) + 
    facet_wrap(~depth) +
    ylab("Proportion choosing target") + 
    xlab("Model Predictions") + 
    geom_smooth(method="lm", aes(group=1)) + 
    geom_abline(slope = 1, intercept = 0, lty=2)
```

### Recursive depth 0-5
```{r}
ggplot(sims_prior, aes(x = preds, y = p, col = expt, pch = object)) +
  geom_pointrange(aes(ymin = cil, ymax = cih)) + 
  xlim(c(0,1)) + ylim(c(0,1)) + 
  facet_wrap(~depth) +
  ylab("Proportion choosing target") + 
  xlab("Model Predictions") + 
  geom_smooth(method="lm", aes(group=1)) + 
  geom_abline(slope = 1, intercept = 0, lty=2)
```

## Correlations
```{r}
sims_prior %>%
  group_by(depth) %>%
  summarise("cor" = cor(p, preds))
```

## Fitting alpha
```{r}
fullData <- fullData %>%
  rowwise %>%
  mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"))
keepIndices <- c("keep", "throwout")
compareIndices  <- which(fullData$tuningData == "keep")

## Parallelize fitting
depths <- seq(0, 5)
priorFit <- mclapply(depths, function(i) { ## parallelize over depths
  rsa.tuneDepthAlpha(fullData, quantityVarName = "object",
                     semanticsVarName = "speaker.p", itemVarName = "query",
                     priorsVarName = "priorValue", groupName = "grouper",
                     compareDataName = "p", compareIndices = compareIndices,
                     depth = i, alphas = seq(1, 6, by = 0.1), usePriorEveryRecurse = FALSE)
  },
  mc.cores = detectCores())
aggregateTuneData <- convertListToDF(priorFit)
```

## Model performance
```{r}
## Get best model performance by alpha, depth
maxCors <- aggregateTuneData %>%
  group_by(depth) %>%
  summarize(maxCor = max(cor),
            alpha = alpha[which.max(cor)])
maxCors
```

## Plot tuning
```{r}
## Plot tuning
ggplot(aggregateTuneData, aes(x = alpha, y = cor, col = as.factor(depth))) +
  geom_point() +
  ylim(0.75, 1) +
  geom_vline(xintercept = maxCors$alpha, lty = 4, col = "grey50") +
  scale_x_continuous(breaks = round(seq(1, 6, by = 0.1)), "alpha") +
  ggtitle("Model performance - priors incorporated")
```

# Simulations WITHOUT priors (recursive depth 0-5)

## Recursive depth sims
```{r}
depths <- seq(0, 5)
sims_NoPrior_temp <- lapply(depths, function(depth) {
  plyr::ddply(fullData, .variables = c("grouper"), rsa.runDf,
            quantityVarName = "object", semanticsVarName = "speaker.p",
            itemVarName = "query", depth = depth) %>%
  rowwise %>%
  mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"),
         depth = depth) %>%
  filter(tuningData == "keep")
})
sims_NoPrior <- convertListToDF(sims_NoPrior_temp)
```

## Simulation plots

### Recursive depth 0-2
```{r}
sims_NoPrior %>%
  filter(depth < 3) %>%
  ggplot(., aes(x = preds, y = p, col = expt, pch = object)) +
    geom_pointrange(aes(ymin = cil, ymax = cih)) + 
    xlim(c(0,1)) + ylim(c(0,1)) + 
    facet_wrap(~depth) +
    ylab("Proportion choosing target") + 
    xlab("Model Predictions") + 
    geom_smooth(method="lm", aes(group=1)) + 
    geom_abline(slope = 1, intercept = 0, lty=2)
```

### Recursive depth 0-5
```{r}
ggplot(sims_NoPrior, aes(x = preds, y = p, col = expt, pch = object)) +
  geom_pointrange(aes(ymin = cil, ymax = cih)) + 
  xlim(c(0,1)) + ylim(c(0,1)) + 
  facet_wrap(~depth) +
  ylab("Proportion choosing target") + 
  xlab("Model Predictions") + 
  geom_smooth(method="lm", aes(group=1)) + 
  geom_abline(slope = 1, intercept = 0, lty=2)
```

## Correlations
```{r}
sims_NoPrior %>%
  group_by(depth) %>%
  summarise("cor" = cor(p, preds))
```

## Fitting alpha
```{r}
## Check that we have fullData and compareIndices for tuning
if (!(inGlobalEnv("fullData") & inGlobalEnv("compareIndices"))) {
  fullData <- fullData %>%
  rowwise %>%
  mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"))
  keepIndices <- c("keep", "throwout")
  compareIndices  <- which(fullData$tuningData == "keep")  
}

## Parallelize fitting
depths <- seq(0, 5)
noPriorFit <- mclapply(depths, function(i) { ## parallelize over depths
  rsa.tuneDepthAlpha(fullData, quantityVarName = "object",
                     semanticsVarName = "speaker.p", itemVarName = "query",
                     compareIndices = compareIndices, compareDataName = "p",
                     groupName = "grouper",
                     depth = i, alphas = seq(1, 6, by = 0.1))
  },
  mc.cores = detectCores())
aggregateTuneData <- convertListToDF(noPriorFit)
```

## Model performance
```{r}
## Get best model performance by alpha, depth
maxCors <- aggregateTuneData %>%
  group_by(depth) %>%
  summarize(maxCor = max(cor),
            alpha = alpha[which.max(cor)])
maxCors
```

## Plot tuning
```{r}
## Plot tuning
ggplot(aggregateTuneData, aes(x = alpha, y = cor, col = as.factor(depth))) +
  geom_point() +
  ylim(0.75, 1) +
  geom_vline(xintercept = maxCors$alpha, lty = 4, col = "grey50") +
  scale_x_continuous(breaks = round(seq(1, 6, by = 0.1)), "alpha") +
  ggtitle("Model performance - no priors")
```

# Propogating errors into model...

## Sims with prior
```{r}
sims_prior %>%
  mutate(errorH = cih - p,
         errorL = p - cil) %>%
  ggplot(., aes(x = preds, y = p, col = expt, pch = object)) +
    geom_errorbarh(aes(xmin = preds - errorL, xmax = preds + errorH)) +
    geom_errorbar(aes(ymin = cil, ymax = cih)) + 
    xlim(c(0,1)) + ylim(c(0,1)) + 
    facet_wrap(~depth) +
    ylab("Proportion choosing target") + 
    xlab("Model Predictions") + 
    geom_smooth(method="lm", aes(group=1)) + 
    geom_abline(slope = 1, intercept = 0, lty=2)
```

## Sims without prior

```{r}
sims_NoPrior %>%
  mutate(errorH = cih - p,
         errorL = p - cil) %>%
  ggplot(., aes(x = preds, y = p, col = expt, pch = object)) +
    geom_errorbarh(aes(xmin = preds - errorL, xmax = preds + errorH)) +
    geom_errorbar(aes(ymin = cil, ymax = cih)) + 
    xlim(c(0,1)) + ylim(c(0,1)) + 
    facet_wrap(~depth) +
    ylab("Proportion choosing target") + 
    xlab("Model Predictions") + 
    geom_smooth(method="lm", aes(group=1)) + 
    geom_abline(slope = 1, intercept = 0, lty=2)
```


# Explicit comparisons with MF sims.Rmd
```{r}
## combine priors and uniform
sims_prior <- sims_prior %>%
  mutate(prior = "prior")
sims_NoPrior <- sims_NoPrior %>%
  mutate(prior = "uniform")
allData <- rbind(sims_prior, sims_NoPrior) %>%
  mutate(model = paste0("L", depth)) %>%
  arrange(prior, query, object, matrix, cond, expt, model)

## Compare with MFs data
mfD <- read.csv("data/modelRuns.csv") %>%
  arrange(prior, query, object, matrix, cond, expt, model)

## Add in MF preds check correlation
allData$mdPreds <- mfD$prediction
allData %>%
  ggplot(aes(x = preds, y = mdPreds, fill = matrix, size = depth)) +
  geom_point(shape = 21, alpha = 0.30)
```
