---
title: "Model Simulations (Trimmed for Paper)"
author: "Ben Peloquin & Mike Frank"
date: "July 6, 2016"
output:
html_document:
toc: true
---

# Helpers and Setup

Load helper functions of data pre-processing and combining. (Also bootstrapping). 

```{r setup2, warning = FALSE, message = FALSE, echo = FALSE}
source("matrices.R")
source("agents.R")
library(rrrsa)
library(dplyr)
library(tidyr)
library(ggplot2)
library(parallel)
library(stats)
library(langcog)
library(xtable)
library(purrr)
knitr::opts_chunk$set(cache=TRUE,
                      warning=FALSE, message=FALSE)

source("helper.R")
```

Global data / settings

```{r globals}
set.seed(1)
ALPHAS <- seq(0, 5, by = 0.1)
DEPTHS <- seq(0, 5)
```

Read in data

```{r main_df}
## This is `d` df from line 128 in sims.Rmd
d <- read.csv("data/models.csv")
```

Get prior counts. 

```{r}
priorCounts <- read.csv("data/prior_counts.csv")
names(priorCounts)[1:3] <- c("foil_cnts", "logical_cnts", "target_cnts")
## Merge with our original data set
d_prior_counts <- merge(d, priorCounts, by = "prior", all = TRUE)
```

Matrices from `matrices.R`

```{r matrix_data}
## Renamed, normalized matrices from matrices.R
simpleM <- normalizeBy(simple, rows = FALSE)
complexM <- normalizeBy(complex, rows = FALSE)
twinsM <- normalizeBy(twins, rows = FALSE)
oddmanM <- normalizeBy(oddman, rows = FALSE)
```

Data pre-processing

NOTE:: To work with rrrsa::runDf we need each matrix to include the literal semantics of all the queries (even if they weren't actually queried)
Look at group 'baserate-63': only 'glasses' is queried, but we need to add the literal semantics for 'hat' and 'mustache' as well.

```{r data_processing}
fullData <- rrrsa_ready_df(d)
```

# Analysis 1: Basic RSA (a la FG2012)

## With no comparison, alpha = 1

Load sims (N=500) and relevel. 

```{r bstrap_data_all_depths}
sims_prior_bstrap_errs <- read.csv("data/sims_prior_bstrap_errs.csv") ## From previous run with 

sims_prior_bstrap_errs$expt[sims_prior_bstrap_errs$expt=="complex"] <- "simple"
sims_prior_bstrap_errs$expt <- factor(sims_prior_bstrap_errs$expt, 
                                      levels = c("baserate","lang","color","simple",
                                                 "twins","oddman"),
                                      labels = c("E5: Base rate","E6: Ling. Frame","E7: Salience",
                                                 "E8: Levels","E9: Twins","E10: Oddman"))
```

Plot bootstrap CIs

```{r plot_bstrap_cis_single_depth}
pdf("../plots/model_basic.pdf", width = 8, height = 6)
ggplot(filter(sims_prior_bstrap_errs,
              depth == 1), 
       aes(x = preds, y = p, col = object)) +
  geom_point() + 
  geom_errorbarh(aes(xmin = ci_hi, xmax = ci_low, height = 0)) +
  geom_errorbar(aes(ymin = cil, ymax = cih, width = 0)) + 
  xlim(c(0,1)) + ylim(c(0,1)) + 
  ylab("Proportion choosing target") + 
  xlab("Model Predictions") + 
  geom_smooth(method="lm", aes(group=1), se=FALSE, col = "black") + 
  geom_abline(slope = 1, intercept = 0, lty=2, "gray") + 
  facet_wrap(~expt) + 
  theme_bw() + 
  scale_color_solarized() + 
  theme(legend.position="bottom")
dev.off()
```

# Analysis 2: Effects of depth

```{r plot_bstrap_cis_all_depths}
pdf("../plots/model_depth.pdf", width = 8, height = 5)
ggplot(filter(sims_prior_bstrap_errs, depth < 3),
       aes(x = preds, y = p, col = object)) +
  geom_point() + 
  geom_errorbarh(aes(xmin = ci_hi, xmax = ci_low, height = 0)) +
  geom_errorbar(aes(ymin = cil, ymax = cih, width = 0)) + 
  xlim(c(0,1)) + ylim(c(0,1)) + 
  ylab("Proportion choosing target") + 
  xlab("Model Predictions") + 
  geom_smooth(method="lm", aes(group=1), se=FALSE, col = "black") + 
  geom_abline(slope = 1, intercept = 0, lty=2, "gray") + 
  facet_grid(depth~expt) + 
  theme_bw() + 
  scale_color_solarized() + 
  theme(legend.position="bottom") +
  scale_x_continuous(breaks=c(.25,.75))
dev.off()
```

## Table of correlations

```{r}
corrs <- sims_prior_bstrap_errs %>%
  group_by(depth) %>%
  do(data.frame(full_corr = cor(.$p,.$preds), 
                no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1], 
                                   .$preds[.$preds != 0 & .$preds != 1])))

print(xtable(corrs, digits = 2), 
      include.rownames=FALSE)
```

# Analysis 3: Fitting alpha

Load alpha tuning. 

```{r}
tune_data <- read.csv("data/alpha_tuning_with_prior.csv")
```

Extract best correlations. 

```{r sims_priors_fitted_cors}
maxCors <- tune_data %>%
  group_by(depth) %>%
  summarize(maxCor = max(cor),
            alpha = alpha[which.max(cor)])
```

Get non-0/1 correlations for this batch. 

```{r}
fullData <- fullData %>% arrange(grouper)

dosim <- function(df) {
  data.frame(fullData) %>% 
    group_by(grouper) %>%
    do(rsa.runDf(data = ., quantityVarName = "object", semanticsVarName = "speaker.p",
                 itemVarName = "query", priorsVarName = "priorValue", 
                 depth = df$depth, alpha = df$alpha,
                 usePriorEveryRecurse = FALSE))
}

sims_alpha <- data.frame(maxCors) %>%
  group_by(depth) %>%
  do(dosim(.)) 

sims_alpha$expt[sims_alpha$expt=="complex"] <- "simple"
sims_alpha$expt <- factor(sims_alpha$expt, 
                                      levels = c("baserate","lang","color","simple",
                                                 "twins","oddman"),
                                      labels = c("E5: Base rate","E6: Ling. Frame","E7: Salience",
                                                 "E8: Levels","E9: Twins","E10: Oddman"))

alpha_corrs <- sims_alpha %>%
  filter(!is.na(p)) %>%
  group_by(depth) %>%
  do(data.frame(full_corr = cor(.$p,.$preds), 
                no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1], 
                                   .$preds[.$preds != 0 & .$preds != 1])))
```

Table.

```{r}
alpha_corrs <- alpha_corrs %>% 
  left_join(maxCors) %>% 
  select(depth, alpha, full_corr, no_zero_corr)

print(xtable(alpha_corrs, digits = 2), 
      include.rownames=FALSE)
```


Figure.

```{r}
tune_data <- tune_data %>%
  mutate(Recursive_depth = as.factor(depth))

pdf("../plots/alpha-fit.pdf", width = 6, height = 4.5)
## Plot tuning (Plot adapted for personal_site)
ggplot(tune_data, aes(x = alpha, y = cor, col=Recursive_depth)) +
  # geom_point(alpha=0.6, size=4) +
  geom_line() + 
  geom_vline(data = maxCors, aes(xintercept=alpha, col = factor(depth)), lty=2)+
  ylab("Correlation") +
  scale_x_continuous(breaks = round(seq(0, 6, by = 0.1)), "alpha (\"greed\") value") +
  scale_color_solarized(name = "Recursive Depth") +
  theme_bw() +
  theme(legend.position="bottom", legend.box="horizontal",
        legend.text=element_text(size=8), legend.direction="horizontal")+ 
  ylim(c(.5,1))
dev.off()
```

## Best fitting alpha


```{r plot_bstrap_cis_single_depth}
# pdf("../plots/model_best.pdf", width = 8, height = 6)

ggplot(filter(sims_prior_bstrap_errs, depth == 5), 
       aes(x = preds, y = p, col = object)) +
  geom_point() + 
  geom_errorbarh(aes(xmin = ci_hi, xmax = ci_low, height = 0)) +
  geom_errorbar(aes(ymin = cil, ymax = cih, width = 0)) + 
  xlim(c(0,1)) + ylim(c(0,1)) + 
  ylab("Proportion choosing target") + 
  xlab("Model Predictions") + 
  geom_smooth(method="lm", aes(group=1), se=FALSE, col = "black") + 
  geom_abline(slope = 1, intercept = 0, lty=2, "gray") + 
  # facet_wrap(~expt) + 
  theme_bw() + 
  scale_color_solarized() + 
  theme(legend.position="bottom")
# dev.off()
```

# Analysis 4: Simulations WITHOUT priors 

Recursive depth sims

```{r sims_no_priors}
sims_NoPrior_temp <- lapply(DEPTHS, function(depth) {
  plyr::ddply(fullData, .variables = c("grouper"), rsa.runDf,
              quantityVarName = "object", semanticsVarName = "speaker.p",
              itemVarName = "query", depth = depth) %>%
    rowwise %>%
    mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"),
           depth = depth) %>%
    filter(tuningData == "keep")
})
sims_NoPrior <- convertListToDF(sims_NoPrior_temp)

sims_NoPrior$expt[sims_NoPrior$expt=="complex"] <- "simple"
sims_NoPrior$expt <- factor(sims_NoPrior$expt, 
                                      levels = c("baserate","lang","color","simple",
                                                 "twins","oddman"),
                                      labels = c("E5: Base rate","E6: Ling. Frame","E7: Salience",
                                                 "E8: Levels","E9: Twins","E10: Oddman"))

```

Recursive depth 0-2

```{r sims_no_priors_plot1, eval = FALSE}
pdf("../plots/model_noprior_depth.pdf", width = 8, height = 5)
ggplot(filter(sims_NoPrior, depth < 3), 
       aes(x = preds, y = p, col = object)) +
  geom_point() + 
  geom_linerange(aes(ymin = cil, ymax = cih)) + 
  xlim(c(0,1)) + ylim(c(0,1)) + 
  ylab("Proportion choosing target") + 
  xlab("Model Predictions") + 
  geom_smooth(method="lm", aes(group=1), se=FALSE, col = "black") + 
  geom_abline(slope = 1, intercept = 0, lty=2, "gray") + 
  facet_grid(depth~expt) + 
  theme_bw() + 
  scale_color_solarized() + 
  theme(legend.position="bottom") +
  scale_x_continuous(breaks=c(.25,.75))
dev.off()

```

## Correlations
```{r sims_no_priors_cors, eval=FALSE}
# sims_NoPrior %>%
#   group_by(depth) %>%
#   summarise("cor" = cor(p, preds)) %>%
#   mutate("alpha" = 1)

noprior_corrs <- sims_NoPrior %>%
  group_by(depth) %>%
  do(data.frame(full_corr = cor(.$p,.$preds), 
                no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1], 
                                   .$preds[.$preds != 0 & .$preds != 1])))

print(xtable(noprior_corrs, digits = 2), 
      include.rownames=FALSE)
```

By Experiment. 

```{r sims_no_priors_cors, eval=FALSE}

noprior_expt_corrs <- sims_NoPrior %>%
  group_by(depth, expt) %>%
  do(data.frame(full_corr = cor(.$p,.$preds), 
                no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1], 
                                   .$preds[.$preds != 0 & .$preds != 1]))) %>%
  select(-no_zero_corr) %>% spread(expt, full_corr) %>%
  mutate(model = "No prior")

alpha_expt_corrs <- sims_alpha %>%
  filter(!is.na(p)) %>%
  group_by(depth, expt) %>%
  do(data.frame(full_corr = cor(.$p,.$preds), 
                no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1], 
                                   .$preds[.$preds != 0 & .$preds != 1]))) %>%
  select(-no_zero_corr) %>% spread(expt, full_corr) %>%
  mutate(model = "Prior, alpha fit")

expt_corrs <- sims_prior_bstrap_errs %>%
  group_by(depth, expt) %>%
  do(data.frame(full_corr = cor(.$p,.$preds), 
                no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1], 
                                   .$preds[.$preds != 0 & .$preds != 1]))) %>%
  select(-no_zero_corr) %>% spread(expt, full_corr) %>%
  mutate(model = "Prior, alpha=1")

all_corrs <- bind_rows(noprior_expt_corrs, alpha_expt_corrs, expt_corrs) %>% 
  arrange(depth) %>%
  filter(depth > 0)

print(xtable(all_corrs[, c(1, 8, 2:7)], digits = 2) , 
      include.rownames=FALSE)
```

## Fitting alpha

<!-- ```{r} -->
<!-- tune_noprior_data <- read.csv("data/alpha_tuning_no_prior.csv") -->
<!-- ``` -->

<!-- Get best model performance by alpha, depth. -->

<!-- ```{r sims_no_priors_fitted_cors} -->
<!-- maxCors_noPriors <- tune_noprior_data %>% -->
<!--   group_by(depth) %>% -->
<!--   summarize(maxCor = max(cor), -->
<!--             alpha = alpha[which.max(cor)]) -->
<!-- ``` -->

<!-- Get non-0/1 correlations for this batch.  -->

<!-- ```{r} -->
<!-- fullData <- fullData %>% arrange(grouper) -->

<!-- dosim_noprior <- function(df) { -->
<!--   data.frame(fullData) %>%  -->
<!--     group_by(grouper) %>% -->
<!--     do(rsa.runDf(data = ., quantityVarName = "object", semanticsVarName = "speaker.p", -->
<!--                  itemVarName = "query",  -->
<!--                  depth = df$depth, alpha = df$alpha, -->
<!--                  usePriorEveryRecurse = FALSE)) -->
<!-- } -->

<!-- sims_alpha <- data.frame(maxCors_noPriors) %>% -->
<!--   group_by(depth) %>% -->
<!--   do(dosim(.))  -->

<!-- alpha_corrs <- sims_alpha %>% -->
<!--   filter(!is.na(p)) %>% -->
<!--   group_by(depth) %>% -->
<!--   do(data.frame(full_corr = cor(.$p,.$preds),  -->
<!--                 no_zero_corr = cor(.$p[.$preds != 0 & .$preds != 1],  -->
<!--                                    .$preds[.$preds != 0 & .$preds != 1]))) -->
<!-- ``` -->

<!-- Table. -->

<!-- ```{r} -->
<!-- alpha_corrs <- alpha_corrs %>%  -->
<!--   left_join(maxCors_noPriors) %>%  -->
<!--   select(depth, alpha, full_corr, no_zero-corr) -->

<!-- print(xtable(alpha_corrs, digits = 2),  -->
<!--       include.rownames=FALSE) -->
<!-- ``` -->



<!-- ## Best NO-priors model performance with fitted alphas -->
<!-- ```{r} -->
<!-- depths_param_data <- maxCors_noPriors %>% -->
<!--   arrange(depth) -->
<!-- best_noPrior_models_fitted_alpha <- convertListToDF(lapply(DEPTHS, function(depth) { ## parallelize over depths -->
<!--   plyr::ddply(fullData, .variables = c("grouper"), rsa.runDf, -->
<!--               quantityVarName = "object", semanticsVarName = "speaker.p", -->
<!--               usePriorEveryRecurse = FALSE, itemVarName = "query", -->
<!--               depth = depths_param_data$depth[depth + 1], alpha = depths_param_data$alpha[depth + 1]) %>% -->
<!--     mutate(tuningData = ifelse(!is.na(count), "keep", "throwout"), -->
<!--            depth = depth) %>% -->
<!--     filter(tuningData == "keep") -->
<!-- })) -->
<!-- ## Quick check -->
<!-- ## cor(best_noPrior_models_fitted_alpha[best_noPrior_models_fitted_alpha$depth == 1, ]$p, best_noPrior_models_fitted_alpha[best_noPrior_models_fitted_alpha$depth == 1, ]$preds) -->
<!-- ``` -->

<!-- ### Plot best No priors model performance with fitted alphas -->
<!-- ```{r} -->
<!-- print("Model performance for recursive depth 0-5 with fitted alphas no priors") -->
<!-- maxCors_noPriors ## performance data -->

<!-- ## plots -->
<!-- ggplot(best_noPrior_models_fitted_alpha, aes(x = preds, y = p, col = expt, pch = object)) + -->
<!--   geom_pointrange(aes(ymin = cil, ymax = cih)) +  -->
<!--   xlim(c(0,1)) + ylim(c(0,1)) +  -->
<!--   facet_wrap(~depth, labeller = label_both) + -->
<!--   ylab("Proportion choosing target") +  -->
<!--   xlab("Model Predictions") +  -->
<!--   geom_smooth(method="lm", aes(group=1)) +  -->
<!--   geom_abline(slope = 1, intercept = 0, lty=2) + -->
<!--   ggtitle("No-prior model performance for recursive depth 0-5 with fitted alphas") + theme_bw() -->
<!-- ``` -->

